---
title: "Comparative Approach: Temporal Question Analysis"
date: "November 2024"
author: "Md Touhidul Islam"

---

```{r, echo=FALSE, message=FALSE, results='hide', cache=T}
# Set locale for consistent date formatting
Sys.setlocale("LC_TIME", "en_US.UTF-8")

# Load required libraries for analysis
library(dplyr)    # For data manipulation
library(ggplot2)  # For visualization
library(ggpubr)   # For publication-ready plots
library(readxl)   # For reading Excel files
library(zoo)      # For time series smoothing
library(DCCA)     # For detrended cross-correlation analysis
library(sandwich) # For robust standard errors
library(tseries)  # For time series tests
library(lmtest)   # For regression diagnostic tests
library(knitr)    # For report generation
library(psych)    # For psychological data analysis
options(scipen = 10)  # Avoid scientific notation in output

# Load custom functions from Functions.R
source("Functions.R")
# Set number of permutations for statistical tests
R <- 10000
# Initialize results dataframe
corrsdf <- NULL
```

# Import YouGov result from excel sheet

```{r}
# Import YouGov survey data from Excel
# Previously downloaded from YouGov API
#download.file("https://yougov.co.uk/_pubapis/v5/uk/trackers/britains-mood-measured-weekly/download/", destfile="YouGov/britains-mood-measured-weekly.xlsx")
Yougovdf <- read_excel("yougovoutput.xlsx", sheet="yougovoutput")
# Standardize date column name
names(Yougovdf)[1] <- "day"
```

# Import BERT models with temporal questions

```{r}
# Set model name for the temporal question approach
model_name = "Base_model"
# Load weather-based temporal question results
filename <- "Result/newsimweather_mean.xlsx"
Weather_data <- read_excel(filename, sheet="transpose")
```

## Result for emotion sad

```{r}
# Analysis for the 'sad' emotion using temporal questions
library(readxl)
library(ggplot2)
library(tidyr)
library(zoo)  # For rolling averages
library(dplyr)  # For data manipulation

# Step 1: Load data
filename <- "Result/newsimweather_mean.xlsx"  # Update the path if needed
berd <- read_excel(filename, sheet = "transpose")

# Ensure first column is "day"
names(berd)[1] <- "day"

# Convert to long format for ggplot
berd_long <- pivot_longer(berd, cols = -day, names_to = "emotion", values_to = "score")

# Convert 'day' to Date format (if not already)
berd_long$day <- as.Date(berd_long$day)

# Step 2: Apply 7-day rolling average for each emotion
berd_long <- berd_long %>%
  group_by(emotion) %>%
  mutate(rolling_score = rollmean(score, k = 7, align = "right", fill = NA)) %>%
  ungroup()

# Step 3: Remove NA values created by rollmean
berd_long <- na.omit(berd_long)

# Step 4: Plot with ggplot2
ggplot(berd_long, aes(x = day, y = rolling_score, color = emotion, group = emotion)) +
  geom_line(linewidth = 1, linetype = "solid") +   # Use solid lines
  #geom_point(size = 2, alpha = 0.6) +             # Add points for visibility
  labs(title = "Emotion Trends (7-day Rolling Avg)", 
       y = "Sentiment Score", 
       x = "Day") +
  theme_minimal() +
  geom_vline(xintercept = as.Date("2023-03-16"), color=rgb(0,0,0,0.5))+
  scale_color_manual(values = rainbow(length(unique(berd_long$emotion)))) +
    geom_vline(xintercept = as.Date(c("2019-09-21", "2019-12-20","2020-03-20", "2020-06-20", "2020-09-20", "2020-12-20","2020-03-21", "2020-06-21", "2020-09-21", "2021-12-20","2021-03-21", "2021-06-21", "2021-09-21", "2021-12-20","2022-03-21", "2022-06-21", "2022-09-21", "2022-12-20")), 
             color = "gray", linetype = "dashed", size = 0.5)



```

##Result for Happy

```{r}
Emotion<-"Happy"
label <- paste(Emotion," in Yougov and ",Emotion," in Bertweet ",model_name)
joind$x <- joind$Happy.x
joind$y <- joind$Happy.y

joind$y <- rollmean(joind$y, k=7, align="right", na.pad = T)
joind <- na.omit(joind)
y_label<-paste("Rescaled ",Emotion)
plotTS(joind, joind, "x", "y",  "darkred","darkblue", "Yougov", model_name, title=label, ylab=y_label, ymin=-2.5, ymax=5,label) 

X <- joind$x
Y <- joind$y
ct <- cor.test(X,Y)
corrsdf <- rbind(corrsdf, data.frame(Emotion, cor=ct$estimate, corlow = ct$conf.int[1], corhigh = ct$conf.int[2]))

results <- analyses(joind, joind, R,label)
results$emotion  <- Emotion
results$method <- "Bert"
results$reweight <- "Yes"
results <- results[, c(16,17,18, seq(1,15))]
```

##Result for Stressed

```{r}
Emotion<-"Stressed"
label <- paste(Emotion," in Yougov and ",Emotion," in Bertweet ",model_name)

joind$x <- joind$Stressed.x
joind$y <- joind$Stressed.y

joind$y <- rollmean(joind$y, k=7, align="right", na.pad = T)
joind <- na.omit(joind)
y_label<-paste("Rescaled ",Emotion)
plotTS(joind, joind, "x", "y", "darkblue", "darkred", model_name, "Yougov", title=label, ylab=y_label, ymin=-2.5, ymax=5,label) 

X <- joind$x
Y <- joind$y
ct <- cor.test(X,Y)
corrsdf <- rbind(corrsdf, data.frame(Emotion, cor=ct$estimate, corlow = ct$conf.int[1], corhigh = ct$conf.int[2]))

results <- analyses(joind, joind, R,label)
results$emotion  <- Emotion
results$method <- "Bert"
results$reweight <- "Yes"
results <- results[, c(16,17,18, seq(1,15))]
```

##Result for Frustrated

```{r}
Emotion<-"Frustrated"
label <- paste(Emotion," in Yougov and ",Emotion," in Bertweet ",model_name)

joind$x <- joind$Frustrated.x
joind$y <- joind$Frustrated.y

joind$y <- rollmean(joind$y, k=7, align="right", na.pad = T)
joind <- na.omit(joind)
y_label<-paste("Rescaled ",Emotion)
plotTS(joind, joind, "x", "y", "darkblue", "darkred", model_name, "Yougov", title=label, ylab=y_label, ymin=-2.5, ymax=5,label) 

X <- joind$x
Y <- joind$y
ct <- cor.test(X,Y)
corrsdf <- rbind(corrsdf, data.frame(Emotion, cor=ct$estimate, corlow = ct$conf.int[1], corhigh = ct$conf.int[2]))

results <- analyses(joind, joind, R,label)
results$emotion  <- Emotion
results$method <- "Bert"
results$reweight <- "Yes"
results <- results[, c(16,17,18, seq(1,15))]FrustratedFrustratedFrustrated
```

##Result for Inspired

```{r}
Emotion<-"Inspired"
label <- paste(Emotion," in Yougov and ",Emotion," in Bertweet ",model_name)

joind$x <- joind$Inspired.x
joind$y <- joind$Inspired.y

joind$y <- rollmean(joind$y, k=7, align="right", na.pad = T)
joind <- na.omit(joind)
y_label<-paste("Rescaled ",Emotion)
plotTS(joind, joind, "x", "y", "darkblue", "darkred", model_name, "Yougov", title=label, ylab=y_label, ymin=-2.5, ymax=5,label) 

X <- joind$x
Y <- joind$y
ct <- cor.test(X,Y)
corrsdf <- rbind(corrsdf, data.frame(Emotion, cor=ct$estimate, corlow = ct$conf.int[1], corhigh = ct$conf.int[2]))

results <- analyses(joind, joind, R, label)
results$emotion  <- Emotion
results$method <- "Bert"
results$reweight <- "Yes"
results <- results[, c(16,17,18, seq(1,15))]
```

##Result for Apathetic

```{r}
Emotion<-"Apathetic"
label <- paste(Emotion," in Yougov and ",Emotion," in Bertweet ",model_name)

joind$x <- joind$Apathetic.x
joind$y <- joind$Apathetic.y

joind$y <- rollmean(joind$y, k=7, align="right", na.pad = T)
joind <- na.omit(joind)
y_label<-paste("Rescaled ",Emotion)
plotTS(joind, joind, "x", "y", "darkblue", "darkred", model_name, "Yougov", title=label, ylab=y_label, ymin=-2.5, ymax=5,label)  

X <- joind$x
Y <- joind$y
ct <- cor.test(X,Y)
corrsdf <- rbind(corrsdf, data.frame(Emotion, cor=ct$estimate, corlow = ct$conf.int[1], corhigh = ct$conf.int[2]))

results <- analyses(joind, joind, R,label)
results$emotion  <- Emotion
results$method <- "Bert"
results$reweight <- "Yes"
results <- results[, c(16,17,18, seq(1,15))]
```

##Result for Lonely

```{r}
Emotion<-"Lonely"
label <- paste(Emotion," in Yougov and ",Emotion," in Bertweet ",model_name)

joind$x <- joind$Lonely.x
joind$y <- joind$Lonely.y

joind$y <- rollmean(joind$y, k=7, align="right", na.pad = T)
joind <- na.omit(joind)
y_label<-paste("Rescaled ",Emotion)
plotTS(joind, joind, "x", "y", "darkblue", "darkred", model_name, "Yougov", title=label, ylab=y_label, ymin=-2.5, ymax=5,label) 

X <- joind$x
Y <- joind$y
ct <- cor.test(X,Y)
corrsdf <- rbind(corrsdf, data.frame(Emotion, cor=ct$estimate, corlow = ct$conf.int[1], corhigh = ct$conf.int[2]))

results <- analyses(joind, joind, R,label)
results$emotion  <- Emotion
results$method <- "Bert"
results$reweight <- "Yes"
results <- results[, c(16,17,18, seq(1,15))]
```

##Result for Optimistic

```{r}
Emotion<-"Optimistic"
label <- paste(Emotion," in Yougov and ",Emotion," in Bertweet ",model_name)

joind$x <- joind$Optimistic.x
joind$y <- joind$Optimistic.y

joind$y <- rollmean(joind$y, k=7, align="right", na.pad = T)
joind <- na.omit(joind)
y_label<-paste("Rescaled ",Emotion)
plotTS(joind, joind, "x", "y", "darkblue", "darkred", model_name, "Yougov", title=label, ylab=y_label, ymin=-2.5, ymax=5,label) 

X <- joind$x
Y <- joind$y
ct <- cor.test(X,Y)
corrsdf <- rbind(corrsdf, data.frame(Emotion, cor=ct$estimate, corlow = ct$conf.int[1], corhigh = ct$conf.int[2]))

results <- analyses(joind, joind, R,label)
results$emotion  <- Emotion
results$method <- "Bert"
results$reweight <- "Yes"
results <- results[, c(16,17,18, seq(1,15))]
```

##Result for Content

```{r}
Emotion<-"Content"
label <- paste(Emotion," in Yougov and ",Emotion," in Bertweet ",model_name)

joind$x <- joind$Content.x
joind$y <- joind$Content.y

joind$y <- rollmean(joind$y, k=7, align="right", na.pad = T)
joind <- na.omit(joind)
y_label<-paste("Rescaled ",Emotion)
plotTS(joind, joind, "x", "y", "darkblue", "darkred", model_name, "Yougov", title=label, ylab=y_label, ymin=-2.5, ymax=5,label) 

X <- joind$x
Y <- joind$y
ct <- cor.test(X,Y)
corrsdf <- rbind(corrsdf, data.frame(Emotion, cor=ct$estimate, corlow = ct$conf.int[1], corhigh = ct$conf.int[2]))

results <- analyses(joind, joind, R,label)
results$emotion  <- Emotion
results$method <- "Bert"
results$reweight <- "Yes"
results <- results[, c(16,17,18, seq(1,15))]
```

##Result for Energetic

```{r}
Emotion<-"Energetic"
label <- paste(Emotion," in Yougov and ",Emotion," in Bertweet ",model_name)

joind$x <- joind$Energetic.x
joind$y <- joind$Energetic.y

joind$y <- rollmean(joind$y, k=7, align="right", na.pad = T)
joind <- na.omit(joind)
y_label<-paste("Rescaled ",Emotion)
plotTS(joind, joind, "x", "y", "darkblue", "darkred", model_name, "Yougov", title=label, ylab=y_label, ymin=-2.5, ymax=5,y_label) 

X <- joind$x
Y <- joind$y
ct <- cor.test(X,Y)
corrsdf <- rbind(corrsdf, data.frame(Emotion, cor=ct$estimate, corlow = ct$conf.int[1], corhigh = ct$conf.int[2]))

results <- analyses(joind, joind, R,label)
results$emotion  <- Emotion
results$method <- "Bert"
results$reweight <- "Yes"
results <- results[, c(16,17,18, seq(1,15))]
```

##Result for Frustrated

```{r}
Emotion<-"Frustrated"
label <- paste(Emotion," in Yougov and ",Emotion," in Bertweet ",model_name)

joind$x <- joind$Frustrated.x
joind$y <- joind$Frustrated.y

joind$y <- rollmean(joind$y, k=7, align="right", na.pad = T)
joind <- na.omit(joind)
y_label<-paste("Rescaled ",Emotion)
plotTS(joind, joind, "x", "y", "darkblue", "darkred", model_name, "Yougov", title=label, ylab=y_label, ymin=-2.5, ymax=5,y_label) 

X <- joind$x
Y <- joind$y
ct <- cor.test(X,Y)
corrsdf <- rbind(corrsdf, data.frame(Emotion, cor=ct$estimate, corlow = ct$conf.int[1], corhigh = ct$conf.int[2]))

results <- analyses(joind, joind, R,label)
results$emotion  <- Emotion
results$method <- "Bert"
results$reweight <- "Yes"
results <- results[, c(16,17,18, seq(1,15))]
```

##Result for Bored

```{r}
Emotion<-"Bored"
label <- paste(Emotion," in Yougov and ",Emotion," in Bertweet ",model_name)

joind$x <- joind$Bored.x
joind$y <- joind$Bored.y

joind$y <- rollmean(joind$y, k=7, align="right", na.pad = T)
joind <- na.omit(joind)
y_label<-paste("Rescaled ",Emotion)
plotTS(joind, joind, "x", "y", "darkblue", "darkred", model_name, "Yougov", title=label, ylab=y_label, ymin=-2.5, ymax=5,y_label) 

X <- joind$x
Y <- joind$y
ct <- cor.test(X,Y)
corrsdf <- rbind(corrsdf, data.frame(Emotion, cor=ct$estimate, corlow = ct$conf.int[1], corhigh = ct$conf.int[2]))

results <- analyses(joind, joind, R,label)
results$emotion  <- Emotion
results$method <- "Bert"
results$reweight <- "Yes"
results <- results[, c(16,17,18, seq(1,15))]
```

#Compareing results

```{r}
epoch<-2
query_type<-"Multi_mean"
similarity<-"Sim"
filename<-getfilename(epoch, query_type,similarity)
filename <-"Result/baseline_same_model.xlsx"
#berd <- read_excel(filename,sheet="transpose")
names(berd)[1] <- "day"
#Yougovdf$day <- as.Date(Yougovdf$day)
Yougovdf$day <- Yougovdf$day
joind = inner_join(Yougovdf, berd,by="day")

joind$x <- joind$Sad.x

joind$y <- joind$Sad.y
```

```{r}
epoch<-2
query_type<-"Multi_median"
similarity<-"NoSim"
#filename<-getfilename(epoch, query_type,similarity)
filename <-"Result/baseline_same_model.xlsx"
berd2 <- read_excel(filename,sheet="transpose")
names(berd2)[1] <- "day"


joind = inner_join(joind, berd2,by="day")

```

```{r}
joind$z <- joind$Sad
```

```{r}
joind$z <- rollmean(joind$z, k=7, align="right", na.pad = T)
joind$y <- rollmean(joind$y, k=7, align="right", na.pad = T)
joind$x <- rollmean(joind$x, k=7, align="right", na.pad = T)
joind$y <- rollmean(joind$y, k=4, align="right", na.pad = T)
```

```{r}
plotTS2(joind,joind, "x", "y","z", "red", "blue","gray", "yougov", "Similarity","Normal", title="Sad with similarity and without similarity", ylab="Rescaled Sadness", ymin=-2.5, ymax=5) 
```

#Total summery

```         
```

```{r}
kable(corrsdf)
library(knitr)

label <- paste("output/",model_name,"correlations_table.html")
label2 <- paste("output/",model_name,"correlations_table.tex")
# Create the table
table_html <- kable(corrsdf, format = "html")

# Save to a file
writeLines(table_html, label)

table_latex <- kable(corrsdf, format = "latex")

# Save to a .tex file
writeLines(table_latex, label2)
```

```{r}

label <- paste("plot/",model_name,"correlations_plot.png")
corrsdf$emotion <- corrsdf$Emotion

p <- ggplot(corrsdf, aes(x=reorder(emotion, cor), y=cor, fill=as.numeric(reorder(emotion, cor))-6, group=emotion)) + 
  geom_col(stat="identity", color="black", 
           position=position_dodge())  +  scale_fill_gradient2(low='blue', mid="purple", high='red') +
  geom_errorbar(aes(ymin=corlow, ymax=corhigh), width=.2,
                 position=position_dodge(.9))  + coord_flip() + theme_bw()
library(ggplot2)


# Save as PNG
ggsave(label, plot = p, width = 8, height = 6, dpi = 300)

```
