---
title: 
date: 
author: 
output: 
  pdf_document:
    keep_tex: true
---

```{r, echo=FALSE, message=FALSE, results='hide', cache=T}
Sys.setlocale("LC_TIME", "en_US.UTF-8")

library(dplyr) #dplyr_1.0.3
library(ggplot2) #ggplot2_3.3.2
library(ggpubr) #ggpubr_0.4.0
library(readxl) #readxl_1.3.1
library(zoo) #zoo_1.8-8
library(DCCA) #DCCA_0.1.1 
library(sandwich) #sandwich_3.0-1
library(tseries) #tseries_0.10-47
library(lmtest) #lmtest_0.9-38 
library(knitr) #knitr_1.30
library(psych) #psych_2.1.6
options(scipen = 10)

source("Functions.R")
R <- 10000
```

```{r}
#download.file("https://yougov.co.uk/_pubapis/v5/uk/trackers/britains-mood-measured-weekly/download/", destfile="YouGov/britains-mood-measured-weekly.xlsx")
Yougovdf <- processYouGov(file="Data/britains-mood-measured-weekly.xlsx", sheet="All adults")
names(Yougovdf)[1] <- "day"
Fdf <- processYouGov(file="Data/britains-mood-measured-weekly.xlsx", sheet="Female")
names(Fdf)[1] <- "day"
Mdf <- processYouGov(file="Data/britains-mood-measured-weekly.xlsx", sheet="Male")
names(Mdf)[1] <- "day"

```

```{r}
#result <- t(read_excel("single/single_quary_epoch2.xlsx"))
result <- read.csv(file="output.csv")
names(result) <- c("day", "bert.result")
result$ro <- rollmean(result$bert.result, k=7, align="right", na.pad = T)
berd <- read_excel("single/single_quary_epoch3.xlsx",sheet="transpose")
names(berd)[1] <- "day"
#berdsad = inner_join(Yougovdf, berd, by="day")

```

Sad with similarity

``` r
```

```{r}
Yougovdf$r <- Yougovdf$sad/100
berd$r <- rollmean(berd$Sad, k=7, align="right", na.pad = T)

plotTS(berd, Yougovdf, "r", "r", "darkblue", "darkred", "Berd", "Yougov", title="Sad in Yougov and Sad in Bertweet (LIWC)", ylab="Rescaled Sadness", ymin=-2.5, ymax=5) 

results <- analyses(berd, Yougovdf, R)
results$emotion  <- "sadness"
results$method <- "LIWC"
results$reweight <- "Yes"
results <- results[, c(16,17,18, seq(1,15))]
```

Happy with similartiy

```{r}
Yougovdf$r <- Yougovdf$happy/100
berd$r <- rollmean(berd$Happy, k=7, align="right", na.pad = T)

plotTS(berd, Yougovdf, "r", "r", "darkblue", "darkred", "Berd", "Yougov", title="Happy in Yougov and Happy in Bertweet", ylab="Rescaled Sadness", ymin=-2.5, ymax=5) 

results <- analyses(berd, Yougovdf, R)
results$emotion  <- "sadness"
results$method <- "LIWC"
results$reweight <- "Yes"
results <- results[, c(16,17,18, seq(1,15))]
```

Stressed with similarity

```{r}
Yougovdf$r <- Yougovdf$stressed/100
berd$r <- rollmean(berd$Stressed, k=7, align="right", na.pad = T)

plotTS(berd, Yougovdf, "r", "r", "darkblue", "darkred", "Berd", "Yougov", title="Stressed in Yougov and Stressed in Bertweet", ylab="Rescaled Sadness", ymin=-2.5, ymax=5) 

results <- analyses(berd, Yougovdf, R)
results$emotion  <- "sadness"
results$method <- "LIWC"
results$reweight <- "Yes"
results <- results[, c(16,17,18, seq(1,15))]
```

Stressed with Feaustrated

```{r}

Yougovdf$r <- Yougovdf$feaustrated/100
berd$r <- rollmean(berd$Feaustrated, k=7, align="right", na.pad = T)

plotTS(berd, Yougovdf, "r", "r", "darkblue", "darkred", "Berd", "Yougov", title="Stressed in Yougov and Stressed in Bertweet", ylab="Rescaled Sadness", ymin=-2.5, ymax=5) 

results <- analyses(berd, Yougovdf, R)
results$emotion  <- "sadness"
results$method <- "LIWC"
results$reweight <- "Yes"
results <- results[, c(16,17,18, seq(1,15))]
```

Stressed with similarity

```{r}

Yougovdf$r <- Yougovdf$bored/100
berd$r <- rollmean(berd$Bored, k=7, align="right", na.pad = T)

plotTS(berd, Yougovdf, "r", "r", "darkblue", "darkred", "Berd", "Yougov", title="Stressed in Yougov and Stressed in Bertweet", ylab="Rescaled Sadness", ymin=-2.5, ymax=5) 

results <- analyses(berd, Yougovdf, R)
results$emotion  <- "sadness"
results$method <- "LIWC"
results$reweight <- "Yes"
results <- results[, c(16,17,18, seq(1,15))]

```

Stressed with Apathetic

```{r}

Yougovdf$r <- Yougovdf$apathetic/100
berd$r <- rollmean(berd$Apathetic, k=7, align="right", na.pad = T)

plotTS(berd, Yougovdf, "r", "r", "darkblue", "darkred", "Berd", "Yougov", title="Stressed in Yougov and Stressed in Bertweet", ylab="Rescaled Sadness", ymin=-2.5, ymax=5) 

results <- analyses(berd, Yougovdf, R)
results$emotion  <- "sadness"
results$method <- "LIWC"
results$reweight <- "Yes"
results <- results[, c(16,17,18, seq(1,15))]
```

Stressed with Lonly

```{r}

Yougovdf$r <- Yougovdf$lonely/100
berd$r <- rollmean(berd$Lonely, k=7, align="right", na.pad = T)

plotTS(berd, Yougovdf, "r", "r", "darkblue", "darkred", "Berd", "Yougov", title="Stressed in Yougov and Stressed in Bertweet", ylab="Rescaled Sadness", ymin=-2.5, ymax=5) 

results <- analyses(berd, Yougovdf, R)
results$emotion  <- "sadness"
results$method <- "LIWC"
results$reweight <- "Yes"
results <- results[, c(16,17,18, seq(1,15))]
```

Stressed with Optimistic

```{r}

Yougovdf$r <- Yougovdf$optimistic/100
berd$r <- rollmean(berd$Optimistic, k=7, align="right", na.pad = T)

plotTS(berd, Yougovdf, "r", "r", "darkblue", "darkred", "Berd", "Yougov", title="Stressed in Yougov and Stressed in Bertweet", ylab="Rescaled Sadness", ymin=-2.5, ymax=5) 

results <- analyses(berd, Yougovdf, R)
results$emotion  <- "sadness"
results$method <- "LIWC"
results$reweight <- "Yes"
results <- results[, c(16,17,18, seq(1,15))]

```

Content

```{r}
Yougovdf$r <- Yougovdf$content/100
berd$r <- rollmean(berd$Content, k=7, align="right", na.pad = T)

plotTS(berd, Yougovdf, "r", "r", "darkblue", "darkred", "Berd", "Yougov", title="Stressed in Yougov and Stressed in Bertweet", ylab="Rescaled Sadness", ymin=-2.5, ymax=5) 

results <- analyses(berd, Yougovdf, R)
results$emotion  <- "sadness"
results$method <- "LIWC"
results$reweight <- "Yes"
results <- results[, c(16,17,18, seq(1,15))]
```

Energetic

```{r}
Yougovdf$r <- Yougovdf$energetic/100
berd$r <- rollmean(berd$Energetic, k=7, align="right", na.pad = T)

plotTS(berd, Yougovdf, "r", "r", "darkblue", "darkred", "Berd", "Yougov", title="Stressed in Yougov and Stressed in Bertweet", ylab="Rescaled Sadness", ymin=-2.5, ymax=5) 

results <- analyses(berd, Yougovdf, R)
results$emotion  <- "sadness"
results$method <- "LIWC"
results$reweight <- "Yes"
results <- results[, c(16,17,18, seq(1,15))]
```

Frustrated

```{r}
Yougovdf$r <- Yougovdf$frustrated/100
berd$r <- rollmean(berd$Frustrated, k=7, align="right", na.pad = T)

plotTS(berd, Yougovdf, "r", "r", "darkblue", "darkred", "Berd", "Yougov", title="Stressed in Yougov and Stressed in Bertweet", ylab="Rescaled Sadness", ymin=-2.5, ymax=5) 

results <- analyses(berd, Yougovdf, R)
results$emotion  <- "sadness"
results$method <- "LIWC"
results$reweight <- "Yes"
results <- results[, c(16,17,18, seq(1,15))]
```

# Sadness

```         
```

```         
```

## Sadness without gender reweight

```{r, echo=FALSE, message=FALSE, fig.width=9, fig.height=3, cache=T}
Tdf <- read.csv("Data/Volume-total.csv")
Tdf2 <- read.csv("Data/Volume-sadness.csv")
TwitterUKdf <- inner_join(Tdf, Tdf2, by="day")
names(TwitterUKdf) <- c("day", "n", "nSadLIWC")
TwitterUKdf$signal <- TwitterUKdf$nSadLIWC/TwitterUKdf$n
TwitterUKdf$w <- rollmean(TwitterUKdf$signal, k=7, align="right", na.pad = T)

Yougovdf$r <- Yougovdf$sad/100

Twittersel <- left_join(Yougovdf, TwitterUKdf, by="day")
Twittersel$r <- Twittersel$w

newres <- analyses(Twittersel, Yougovdf, R)
newres$emotion  <- "sadness"
newres$method <- "LIWC"
newres$reweight <- "No"

results <- rbind(results, newres)
```

## Sadness: men

```{r, echo=FALSE, message=FALSE, fig.width=9, fig.height=3, cache=T}
Tdf <- read.csv("Data/genderVolume-total.csv")
Tdf2 <- read.csv("Data/genderVolume-sadness.csv")
TwitterUKdf <- inner_join(Tdf, Tdf2, by="day")
names(TwitterUKdf) <- c("day", "n.male", "n.female", "nLIWC.male",  "nLIWC.female")

TwitterUKdf$signal <- TwitterUKdf$nLIWC.male/TwitterUKdf$n.male
TwitterUKdf$w <- rollmean(TwitterUKdf$signal, k=7, align="right", na.pad = T)

Mdf$r <- Mdf$sad/100

Twittersel <- left_join(Mdf, TwitterUKdf, by="day")
Twittersel$r <- Twittersel$w

genderresults <- analyses(Twittersel, Mdf, R)
genderresults$emotion  <- "sadness"
genderresults$gender <- "male"
genderresults <- genderresults[, c(16,17, seq(1,15))]
```

## Sadness: women

```{r, echo=FALSE, message=FALSE, fig.width=9, fig.height=3, cache=T}
TwitterUKdf$signal <- TwitterUKdf$nLIWC.female/TwitterUKdf$n.female
TwitterUKdf$w <- rollmean(TwitterUKdf$signal, k=7, align="right", na.pad = T)

Fdf$r <- Fdf$sad/100

Twittersel <- left_join(Fdf, TwitterUKdf, by="day")
Twittersel$r <- Twittersel$w

nres <- analyses(Twittersel, Fdf, R)
nres$emotion <- "sadness"
nres$gender <- "female"
genderresults <- rbind(genderresults, nres)
```

## Sadness Roberta

```{r, echo=FALSE, message=FALSE, fig.width=5, fig.height=3.5, cache=T}
genderdf <- read.csv("Data/RobertaAggGender.csv")

genderdf %>% filter(gender=="male") -> maledf
maledf$signalM <- maledf$mnsadness
genderdf %>% filter(gender=="female") -> femaledf
femaledf$signalF <- femaledf$mnsadness
TwitterUKdf <- inner_join(maledf, femaledf, by="date")
TwitterUKdf$signal <- TwitterUKdf$signalF+TwitterUKdf$signalM
names(TwitterUKdf)[2] <- "day"

TwitterUKdf$w <- rollmean(TwitterUKdf$signal, k=7, align="right", na.pad = T)

Yougovdf$r <- Yougovdf$sad/100

Twittersel <- left_join(Yougovdf, TwitterUKdf, by="day")
Twittersel$r <- Twittersel$w

plotTS(Twittersel, Yougovdf, "r", "r","darkorange", "darkred","Twitter", "Yougov", title="Sad in Yougov and Sad in Twitter (Roberta)", ylab="Rescaled Sadness", ymin=-2.5, ymax=5) 

nres <- analyses(Twittersel, Yougovdf, R)
nres$emotion  <- "sadness"
nres$method <- "RoBERTa"
nres$reweight <- "Yes"
results <- rbind(results, nres)
```

## Sadness Roberta without gender reweight

```{r, echo=FALSE, message=FALSE, fig.width=9, fig.height=3, cache=T}
Tdf <- read.csv("Data/RobertaAgg.csv")
TwitterUKdf <- data.frame(Tdf$date, Tdf$n, Tdf$mnsadness)
names(TwitterUKdf) <- c("day", "n", "signal")
TwitterUKdf$w <- rollmean(TwitterUKdf$signal, k=7, align="right", na.pad = T)

Yougovdf$r <- Yougovdf$sad/100

Twittersel <- left_join(Yougovdf, TwitterUKdf, by="day")
Twittersel$r <- Twittersel$w

nres <- analyses(Twittersel, Yougovdf, R)
nres$emotion  <- "sadness"
nres$method <- "RoBERTa"
nres$reweight <- "No"
results <- rbind(results, nres)
```

\newpage

# Scared

```{r, echo=FALSE, message=FALSE, fig.width=5, fig.height=3.5, cache=T}
Tdf <- read.csv("Data/genderVolume-total.csv")
Tdf2 <- read.csv("Data/genderVolume-anxiety.csv")
TwitterUKdf <- inner_join(Tdf, Tdf2, by="day")
names(TwitterUKdf) <- c("day", "n.male", "n.female", "nLIWC.male",  "nLIWC.female")
TwitterUKdf$signal <- TwitterUKdf$nLIWC.male/TwitterUKdf$n.male + TwitterUKdf$nLIWC.female/TwitterUKdf$n.female
TwitterUKdf$w <- rollmean(TwitterUKdf$signal, k=7, align="right", na.pad = T)

Yougovdf$r <- Yougovdf$scared/100

Twittersel <- left_join(Yougovdf, TwitterUKdf, by="day")
Twittersel$r <- Twittersel$w

plotTS(Twittersel, Yougovdf, "r", "r", "darkblue", "darkred", "Twitter", "Yougov", title="Scared in Yougov and Anxiety in Twitter (LIWC)", ylab="Rescaled Anxiety", ymin=-2.5, ymax=7.5) 

nres <- analyses(Twittersel, Yougovdf, R)
nres$emotion  <- "anxiety"
nres$method <- "LIWC"
nres$reweight <- "Yes"
results <- rbind(results, nres)
```

## Scared without gender reweight

```{r, echo=FALSE, message=FALSE, fig.width=9, fig.height=3, cache=T}
Tdf <- read.csv("Data/Volume-total.csv")
Tdf2 <- read.csv("Data/Volume-anxiety.csv")
TwitterUKdf <- inner_join(Tdf, Tdf2, by="day")
names(TwitterUKdf) <- c("day", "n", "nAnxLIWC")
TwitterUKdf$signal <- TwitterUKdf$nAnxLIWC/TwitterUKdf$n
TwitterUKdf$w <- rollmean(TwitterUKdf$signal, k=7, align="right", na.pad = T)

Yougovdf$r <- Yougovdf$scared/100

Twittersel <- left_join(Yougovdf, TwitterUKdf, by="day")
Twittersel$r <- Twittersel$w

nres <- analyses(Twittersel, Yougovdf, R)
nres$emotion  <- "anxiety"
nres$method <- "LIWC"
nres$reweight <- "No"
results <- rbind(results, nres)
```

## Scared: men

```{r, echo=FALSE, message=FALSE, fig.width=9, fig.height=3, cache=T}
Tdf <- read.csv("Data/genderVolume-total.csv")
Tdf2 <- read.csv("Data/genderVolume-anxiety.csv")
TwitterUKdf <- inner_join(Tdf, Tdf2, by="day")
names(TwitterUKdf) <- c("day", "n.male", "n.female", "nLIWC.male",  "nLIWC.female")
TwitterUKdf$signal <- TwitterUKdf$nLIWC.male/TwitterUKdf$n.male
TwitterUKdf$w <- rollmean(TwitterUKdf$signal, k=7, align="right", na.pad = T)

Mdf$r <- Mdf$scared/100

Twittersel <- left_join(Mdf, TwitterUKdf, by="day")
Twittersel$r <- Twittersel$w

nres <- analyses(Twittersel, Mdf, R)
nres$emotion <- "anxiety"
nres$gender <- "male"
genderresults <- rbind(genderresults, nres)
```

## Scared: women

```{r, echo=FALSE, message=FALSE, fig.width=9, fig.height=3, cache=T}
TwitterUKdf$signal <- TwitterUKdf$nLIWC.female/TwitterUKdf$n.female
TwitterUKdf$w <- rollmean(TwitterUKdf$signal, k=7, align="right", na.pad = T)

Fdf$r <- Fdf$scared/100

Twittersel <- left_join(Fdf, TwitterUKdf, by="day")
Twittersel$r <- Twittersel$w


nres <- analyses(Twittersel, Fdf, R)
nres$emotion <- "anxiety"
nres$gender <- "female"
genderresults <- rbind(genderresults, nres)
```

## Scared Roberta

```{r, echo=FALSE, message=FALSE, fig.width=5, fig.height=3.5, cache=T}
genderdf <- read.csv("Data/RobertaAggGender.csv")

genderdf %>% filter(gender=="male") -> maledf
maledf$signalM <- maledf$mnfear
genderdf %>% filter(gender=="female") -> femaledf
femaledf$signalF <- femaledf$mnfear
TwitterUKdf <- inner_join(maledf, femaledf, by="date")
TwitterUKdf$signal <- TwitterUKdf$signalF+TwitterUKdf$signalM
names(TwitterUKdf)[2] <- "day"

TwitterUKdf$w <- rollmean(TwitterUKdf$signal, k=7, align="right", na.pad = T)

Yougovdf$r <- Yougovdf$scared/100

Twittersel <- left_join(Yougovdf, TwitterUKdf, by="day")
Twittersel$r <- Twittersel$w

plotTS(Twittersel, Yougovdf, "r", "r", "darkorange", "darkred", "Twitter", "Yougov", title="Scared in Yougov and Fear in Twitter (Roberta)", ylab="Rescaled Fear", ymin=-2.5, ymax=7.5) 


nres <- analyses(Twittersel, Yougovdf, R)
nres$emotion  <- "anxiety"
nres$method <- "RoBERTa"
nres$reweight <- "Yes"
results <- rbind(results, nres)
```

## Scared Roberta without gender reweight

```{r, echo=FALSE, message=FALSE, fig.width=9, fig.height=3, cache=T}
Tdf <- read.csv("Data/RobertaAgg.csv")
TwitterUKdf <- data.frame(Tdf$date, Tdf$n, Tdf$mnfear)
names(TwitterUKdf) <- c("day", "n", "signal")
TwitterUKdf$w <- rollmean(TwitterUKdf$signal, k=7, align="right", na.pad = T)

Yougovdf$r <- Yougovdf$scared/100

Twittersel <- left_join(Yougovdf, TwitterUKdf, by="day")
Twittersel$r <- Twittersel$w

nres <- analyses(Twittersel, Yougovdf, R)
nres$emotion  <- "anxiety"
nres$method <- "RoBERTa"
nres$reweight <- "No"
results <- rbind(results, nres)
```

\newpage

# Happy

```{r, echo=FALSE, message=FALSE, fig.width=5, fig.height=3.5, cache=T}
Tdf <- read.csv("Data/genderVolume-total.csv")
Tdf2 <- read.csv("Data/genderVolume-posemo.csv")
TwitterUKdf <- inner_join(Tdf, Tdf2, by="day")
names(TwitterUKdf) <- c("day", "n.male", "n.female", "nLIWC.male",  "nLIWC.female")
TwitterUKdf$signal <- TwitterUKdf$nLIWC.male/TwitterUKdf$n.male + TwitterUKdf$nLIWC.female/TwitterUKdf$n.female
TwitterUKdf$w <- rollmean(TwitterUKdf$signal, k=7, align="right", na.pad = T)

Yougovdf$r <- Yougovdf$happy/100

Twittersel <- left_join(Yougovdf, TwitterUKdf, by="day")
Twittersel$r <- Twittersel$w

plotTS(Twittersel, Yougovdf, "r", "r", "darkblue", "darkred",  "Twitter", "Yougov", title="Happy in Yougov and Positive in Twitter (LIWC)", ylab="Rescaled Positive", ymin=-3.5, ymax=4)

nres <- analyses(Twittersel, Yougovdf, R)
nres$emotion  <- "joy"
nres$method <- "LIWC"
nres$reweight <- "Yes"
results <- rbind(results, nres)
```

## Happy without gender reweight

```{r, echo=FALSE, message=FALSE, fig.width=9, fig.height=3, cache=T}
Tdf <- read.csv("Data/Volume-total.csv")
Tdf2 <- read.csv("Data/Volume-posemo.csv")
TwitterUKdf <- inner_join(Tdf, Tdf2, by="day")
names(TwitterUKdf) <- c("day", "n", "nPosLIWC")
TwitterUKdf$signal <- TwitterUKdf$nPosLIWC/TwitterUKdf$n
TwitterUKdf$w <- rollmean(TwitterUKdf$signal, k=7, align="right", na.pad = T)

Yougovdf$r <- Yougovdf$happy/100

Twittersel <- left_join(Yougovdf, TwitterUKdf, by="day")
Twittersel$r <- Twittersel$w

nres <- analyses(Twittersel, Yougovdf, R)
nres$emotion  <- "joy"
nres$method <- "LIWC"
nres$reweight <- "No"
results <- rbind(results, nres)
```

## Happy: men

```{r, echo=FALSE, message=FALSE, fig.width=9, fig.height=3, cache=T}
Tdf <- read.csv("Data/genderVolume-total.csv")
Tdf2 <- read.csv("Data/genderVolume-posemo.csv")
TwitterUKdf <- inner_join(Tdf, Tdf2, by="day")
names(TwitterUKdf) <- c("day", "n.male", "n.female", "nLIWC.male",  "nLIWC.female")
TwitterUKdf$signal <- TwitterUKdf$nLIWC.male/TwitterUKdf$n.male
TwitterUKdf$w <- rollmean(TwitterUKdf$signal, k=7, align="right", na.pad = T)

Mdf$r <- Mdf$happy/100

Twittersel <- left_join(Mdf, TwitterUKdf, by="day")
Twittersel$r <- Twittersel$w

nres <- analyses(Twittersel, Mdf, R)
nres$emotion <- "joy"
nres$gender <- "male"
genderresults <- rbind(genderresults, nres)
```

## Happy: women

```{r, echo=FALSE, message=FALSE, fig.width=9, fig.height=3, cache=T}
TwitterUKdf$signal <- TwitterUKdf$nLIWC.female/TwitterUKdf$n.female
TwitterUKdf$w <- rollmean(TwitterUKdf$signal, k=7, align="right", na.pad = T)

Fdf$r <- Fdf$happy/100

Twittersel <- left_join(Fdf, TwitterUKdf, by="day")
Twittersel$r <- Twittersel$w

nres <- analyses(Twittersel, Fdf, R)
nres$emotion <- "joy"
nres$gender <- "female"
genderresults <- rbind(genderresults, nres)

```

## Happy Roberta

```{r, echo=FALSE, message=FALSE, fig.width=5, fig.height=3.5, cache=T}
genderdf <- read.csv("Data/RobertaAggGender.csv")

genderdf %>% filter(gender=="male") -> maledf
maledf$signalM <- maledf$mnjoy
genderdf %>% filter(gender=="female") -> femaledf
femaledf$signalF <- femaledf$mnjoy
TwitterUKdf <- inner_join(maledf, femaledf, by="date")
TwitterUKdf$signal <- TwitterUKdf$signalF+TwitterUKdf$signalM
names(TwitterUKdf)[2] <- "day"

TwitterUKdf$w <- rollmean(TwitterUKdf$signal, k=7, align="right", na.pad = T)

Yougovdf$r <- Yougovdf$happy/100

Twittersel <- left_join(Yougovdf, TwitterUKdf, by="day")
Twittersel$r <- Twittersel$w

plotTS(Twittersel, Yougovdf, "r", "r", "darkorange", "darkred", "Twitter", "Yougov", title="Happy in Yougov and Joy in Twitter (Roberta)", ylab="Rescaled Joy", ymin=-3.5, ymax=4)


nres <- analyses(Twittersel, Yougovdf, R)
nres$emotion  <- "joy"
nres$method <- "RoBERTa"
nres$reweight <- "Yes"
results <- rbind(results, nres)
```

## Happy Roberta without gender reweight

```{r, echo=FALSE, message=FALSE, fig.width=9, fig.height=3, cache=T}
Tdf <- read.csv("Data/RobertaAgg.csv")
TwitterUKdf <- data.frame(Tdf$date, Tdf$n, Tdf$mnjoy)
names(TwitterUKdf) <- c("day", "n", "signal")
TwitterUKdf$w <- rollmean(TwitterUKdf$signal, k=7, align="right", na.pad = T)

Yougovdf$r <- Yougovdf$happy/100

Twittersel <- left_join(Yougovdf, TwitterUKdf, by="day")
Twittersel$r <- Twittersel$w

nres <- analyses(Twittersel, Yougovdf, R)
nres$emotion  <- "joy"
nres$method <- "RoBERTa"
nres$reweight <- "No"
results <- rbind(results, nres)
```

# Summary macroscopes

```{r, echo=FALSE, message=FALSE, fig.width=9, fig.height=3, cache=T}
results %>% select(emotion, method, reweight, rh, rhlow, rhhigh, rhp, rhpperm, rp, rplow, rphigh, rpp, rppperm)%>% kable(digits=3)

results %>% select(emotion, method, reweight, dcca, dccap, beta, betap, KSp)%>% kable(digits=3)

genderresults %>% select(emotion, gender, rh, rhlow, rhhigh, rhp, rhpperm, rp, rplow, rphigh, rpp, rppperm)%>% kable(digits=3)

genderresults %>% select(emotion, gender, dcca, dccap, beta, betap, KSp)%>% kable(digits=3)
```

# YouGov and I feel

```{r, echo=FALSE, message=FALSE, fig.width=9, fig.height=3, cache=T}
corrsdf <- NULL

inds <- c("happy","sad","energetic","apathetic","inspired","frustrated","optimistic", "stressed","content","bored","lonely","scared")

for (ind in inds)
{
print(ind)
Yougovdf$r <- Yougovdf[[ind]]/100

Tdf <- read.csv("Data/Volume-total.csv")
Tdf2 <- read.csv(paste0("Data/Volume-",ind,"YouGov.csv"))
TwitterUKdf <- inner_join(Tdf, Tdf2, by="day")
names(TwitterUKdf) <- c("day", "n", "ntweets")
TwitterUKdf$signal <- TwitterUKdf$ntweets/TwitterUKdf$n
TwitterUKdf$w <- rollmean(TwitterUKdf$signal, k=7, align="right", na.pad = T)
TwitterUKdf$ntweetstotal <- rollsum(TwitterUKdf$ntweets, k=7, align="right", na.pad = T)

Twittersel <- left_join(Yougovdf, TwitterUKdf, by="day")
Twittersel$r <- Twittersel$w

X <- Twittersel$r
Y <- Yougovdf$r
ct <- cor.test(X,Y)
print(ct)

print("Corr perm test p-val:")
rndR <- permcor(X,Y,R) # do a permutation test 
print((sum(rndR>=cor(X,Y))+1)/R)

corrsdf <- rbind(corrsdf, data.frame(ind, cor=ct$estimate, corlow = ct$conf.int[1], corhigh = ct$conf.int[2], YGmean=mean(Yougovdf$r), TWmean=mean(Twittersel$ntweetstotal)))

}
```

```{r, echo=FALSE, message=FALSE, fig.width=9, fig.height=3, cache=T, results='asis'}
kable(corrsdf)
```

```{r, echo=FALSE, message=FALSE, fig.width=7, fig.height=3.5, cache=T}
corrsdf$emotion <- corrsdf$ind

ggplot(corrsdf, aes(x=reorder(emotion, cor), y=cor, fill=as.numeric(reorder(emotion, cor))-6, group=emotion)) + 
  geom_col(stat="identity", color="black", 
           position=position_dodge())  +  scale_fill_gradient2(low='blue', mid="purple", high='red') +
  geom_errorbar(aes(ymin=corlow, ymax=corhigh), width=.2,
                 position=position_dodge(.9))  + coord_flip() + theme_bw()


```

## With gender rescaling

```{r, echo=FALSE, message=FALSE, fig.width=9, fig.height=3, cache=T}
corrsdf <- NULL

inds <- c("happy","sad","energetic","apathetic","inspired","frustrated","optimistic", "stressed","content","bored","lonely","scared")

for (ind in inds)
{
print(ind)
Yougovdf$r <- Yougovdf[[ind]]/100

Tdf <- read.csv("Data/genderVolume-total.csv")
Tdf2 <- read.csv(paste0("Data/genderVolume-",ind,"YouGov.csv"))
TwitterUKdf <- inner_join(Tdf, Tdf2, by="day")
names(TwitterUKdf) <- c("day", "maletotal", "femaletotal","male", "female")
TwitterUKdf$signal <- TwitterUKdf$male/TwitterUKdf$maletotal + TwitterUKdf$female/TwitterUKdf$femaletotal
TwitterUKdf$w <- rollmean(TwitterUKdf$signal, k=7, align="right", na.pad = T)

Twittersel <- left_join(Yougovdf, TwitterUKdf, by="day")
Twittersel$r <- Twittersel$w

X <- Twittersel$r
Y <- Yougovdf$r
ct <- cor.test(X,Y)
print(ct)

print("Corr perm test p-val:")
rndR <- permcor(X,Y,R) # do a permutation test 
print((sum(rndR>=cor(X,Y))+1)/R)

corrsdf <- rbind(corrsdf, data.frame(ind, cor=ct$estimate, corlow = ct$conf.int[1], corhigh = ct$conf.int[2], YGmean=mean(Yougovdf$r)))

}


```

```{r, echo=FALSE, message=FALSE, fig.width=9, fig.height=3, cache=T, results='asis'}
kable(corrsdf)
```

```{r, echo=FALSE, message=FALSE, fig.width=7, fig.height=3.5, cache=T}
corrsdf$emotion <- corrsdf$ind

ggplot(corrsdf, aes(x=reorder(emotion, cor), y=cor, fill=as.numeric(reorder(emotion, cor))-6, group=emotion)) + 
  geom_col(stat="identity", color="black", 
           position=position_dodge())  +  scale_fill_gradient2(low='blue', mid="purple", high='red') +
  geom_errorbar(aes(ymin=corlow, ymax=corhigh), width=.2,
                 position=position_dodge(.9))  + coord_flip() + theme_bw()
```

# Social signals as 3rd person

```{r, echo=FALSE, message=FALSE, results='hide', cache=T, eval=F}
Yougovdf <- processYouGov(file="YouGov/britains-mood-measured-weekly.xlsx", sheet="All adults")
names(Yougovdf)[1] <- "day"

Tdf <- read.csv("TwitterAggregates/Volume-total.csv")

Tdf2 <- read.csv("TwitterAggregates/Volume-sadness.csv")
names(Tdf2) <- c("day", "nsad")
Tdf <- inner_join(Tdf, Tdf2)

Tdf2 <- read.csv("TwitterAggregates/Volume-anxiety.csv")
names(Tdf2) <- c("day", "nanx")
Tdf <- inner_join(Tdf, Tdf2)

Tdf2 <- read.csv("TwitterAggregates/Volume-posemo.csv")
names(Tdf2) <- c("day", "npos")
Tdf <- inner_join(Tdf, Tdf2)

Tdf2 <- read.csv("TwitterAggregates/Volume-3rdperson.csv")
names(Tdf2) <- c("day", "n3rd")
Tdf <- inner_join(Tdf, Tdf2)

Tdf2 <- read.csv("TwitterAggregates/Volume-3rdpersonanx.csv")
names(Tdf2) <- c("day", "n3rdanx")
Tdf <- inner_join(Tdf, Tdf2)

Tdf2 <- read.csv("TwitterAggregates/Volume-3rdpersonsad.csv")
names(Tdf2) <- c("day", "n3rdsad")
Tdf <- inner_join(Tdf, Tdf2)

Tdf2 <- read.csv("TwitterAggregates/Volume-3rdpersonposemo.csv")
names(Tdf2) <- c("day", "n3rdpos")
Tdf <- inner_join(Tdf, Tdf2)

Tdf %>% filter(as.Date(day)>min(as.Date(Yougovdf$day))-7 & as.Date(day) <= max(as.Date(Yougovdf$day))) -> Tdf
```

```{r, echo=FALSE, message=FALSE, cache=T, eval=F}
print("Total fraction of 3rd person tweets:")
sum(Tdf$n3rd)/sum(Tdf$ntweets)

print("Total fraction of 3rd person tweets in anxiety:")
n3rd <- sum(Tdf$n3rdanx)/sum(Tdf$nanx)
n3rd

print("Total fraction of 3rd person tweets in not anxiety:")
n3rdnot <- sum(Tdf$n3rd-Tdf$n3rdanx)/sum(Tdf$ntweets-Tdf$nanx)
n3rdnot

print("% diff:")
(n3rd-n3rdnot)/n3rdnot*100
prop.test(c(sum(Tdf$n3rdanx),sum(Tdf$n3rd-Tdf$n3rdanx)) , c(sum(Tdf$nanx), sum(Tdf$ntweets-Tdf$nanx)))

print("Total fraction of 3rd person tweets in sadness:")
n3rd <- sum(Tdf$n3rdsad)/sum(Tdf$nsad)
n3rd

print("Total fraction of 3rd person tweets in not sadness:")
n3rdnot <- sum(Tdf$n3rd-Tdf$n3rdsad)/sum(Tdf$ntweets-Tdf$nsad)
n3rdnot

print("% diff:")
(n3rd-n3rdnot)/n3rdnot*100
prop.test(c(sum(Tdf$n3rdsad),sum(Tdf$n3rd-Tdf$n3rdsad)) , c(sum(Tdf$nsad), sum(Tdf$ntweets-Tdf$nsad)))



print("Total fraction of 3rd person tweets in positive:")
n3rd <- sum(Tdf$n3rdpos)/sum(Tdf$npos)
n3rd

print("Total fraction of 3rd person tweets in not positive:")
n3rdnot <- sum(Tdf$n3rd-Tdf$n3rdpos)/sum(Tdf$ntweets-Tdf$npos)
n3rdnot

print("% diff:")
(n3rd-n3rdnot)/n3rdnot*100
prop.test(c(sum(Tdf$n3rdpos),sum(Tdf$n3rd-Tdf$n3rdpos)) , c(sum(Tdf$npos), sum(Tdf$ntweets-Tdf$npos)))


```

```{r, echo=FALSE, message=FALSE, cache=T, eval=F}
df <- read.csv("TwitterAggregates/LIWC_NER.csv")

print("Total fraction of 3rd person tweets (NER):")
sum(df$ref)/nrow(df)

print("Total fraction of 3rd person tweets in anxiety:")
f <- df$anx>0
n3rd <- sum(df$ref[f])/sum(f)
n3rd

print("Total fraction of 3rd person tweets in not anxiety:")
f <- df$anx==0
n3rdnot <- sum(df$ref[f])/sum(f)
n3rdnot

print("% diff:")
(n3rd-n3rdnot)/n3rdnot*100
prop.test(c(sum(df$ref[df$anx>0]),sum(df$ref[df$anx==0])) , c(sum(df$anx>0), sum(df$anx==0)))

print("Total fraction of 3rd person tweets in sadness:")
f <- df$sad>0
n3rd <- sum(df$ref[f])/sum(f)
n3rd

print("Total fraction of 3rd person tweets in not sadness:")
f <- df$sad==0
n3rdnot <- sum(df$ref[f])/sum(f)
n3rdnot

print("% diff:")
(n3rd-n3rdnot)/n3rdnot*100
prop.test(c(sum(df$ref[df$sad>0]),sum(df$ref[df$sad==0])) , c(sum(df$sad>0), sum(df$sad==0)))

print("Total fraction of 3rd person tweets in positive:")
f <- df$posemo>0
n3rd <- sum(df$ref[f])/sum(f)
n3rd

print("Total fraction of 3rd person tweets in not positive:")
f <- df$posemo==0
n3rdnot <- sum(df$ref[f])/sum(f)
n3rdnot


print("% diff:")
(n3rd-n3rdnot)/n3rdnot*100
prop.test(c(sum(df$ref[df$posemo>0]),sum(df$ref[df$posemo==0])) , c(sum(df$posemo>0), sum(df$posemo==0)))

```

# Election poll correlations

```{r, echo=FALSE, message=FALSE, cache=T}
df <- read.csv("Data/USPollsAligned.csv")
cor.test(df$YouGovBiden, df$HillBiden)
cor.test(df$YouGovTrump, df$HillTrump)

cor.test(df$YouGovBiden, df$RasmussenBiden)
cor.test(df$YouGovTrump, df$RasmussenTrump)

cor.test(df$RasmussenBiden, df$HillBiden)
cor.test(df$RasmussenTrump, df$HillTrump)
```

# LIWC 3rd person analysis

```{r, echo=FALSE, message=FALSE, cache=T, fig.width=4, fig.height=4, results='asis'}
df <- read.csv("Data/LIWC_1M.csv", stringsAsFactors = F)

model <- glm((shehe+they)>0 ~  (anx>0) + (sad>0) + (posemo>0), df, family="binomial")
model1 <- glm((shehe+they)>0 ~ log(WC) + (anx>0) + (sad>0) + (posemo>0), df, family="binomial")
model2 <- glm((shehe+they)>0 ~ log(WC) + (adj>0), df, family="binomial")

library(texreg)
texreg(list(model, model1, model2))
```

# Analysis of central users

```{r, echo=FALSE, message=FALSE, fig.width=5, fig.height=3.5, cache=T}
Tdf <- read.csv("Data/genderVolume-total.csv")
Tdf2 <- read.csv("Data/genderVolume-sadness.csv")
TwitterUKdf <- inner_join(Tdf, Tdf2, by="day")
names(TwitterUKdf) <- c("day", "n.male", "n.female", "nLIWC.male",  "nLIWC.female")
TwitterUKdf$signal <- TwitterUKdf$nLIWC.male/TwitterUKdf$n.male + TwitterUKdf$nLIWC.female/TwitterUKdf$n.female
TwitterUKdf$w <- rollmean(TwitterUKdf$signal, k=7, align="right", na.pad = T)
Yougovdf$r <- Yougovdf$sad/100
Twittersel <- left_join(Yougovdf, TwitterUKdf, by="day")

Tdf <- read.csv("Data/genderAuthors-total10K.csv")
Tdf2 <- read.csv("Data/genderAuthors-sadness10K.csv")
TwitterUKdf10K <- inner_join(Tdf, Tdf2, by="day")
names(TwitterUKdf10K) <- c("day", "n.male", "n.female", "nLIWC.male",  "nLIWC.female")
TwitterUKdf10K$signal <- TwitterUKdf10K$nLIWC.male/TwitterUKdf10K$n.male + TwitterUKdf10K$nLIWC.female/TwitterUKdf10K$n.female
TwitterUKdf10K$w10K <- rollmean(TwitterUKdf10K$signal, k=7, align="right", na.pad = T)

Twittersel <- inner_join(Twittersel, TwitterUKdf10K, by="day")

cor.test(Twittersel$r, Twittersel$w)
cor.test(Twittersel$r, Twittersel$w10K)
r.test(n=nrow(Twittersel), r12=cor(Twittersel$r,Twittersel$w10K), r13=cor(Twittersel$r, Twittersel$w), r23=cor(Twittersel$w, Twittersel$w10K), twotailed = F)
```

```{r, echo=FALSE, message=FALSE, fig.width=5, fig.height=3.5, cache=T}
Tdf <- read.csv("Data/genderVolume-total.csv")
Tdf2 <- read.csv("Data/genderVolume-anxiety.csv")
TwitterUKdf <- inner_join(Tdf, Tdf2, by="day")
names(TwitterUKdf) <- c("day", "n.male", "n.female", "nLIWC.male",  "nLIWC.female")
TwitterUKdf$signal <- TwitterUKdf$nLIWC.male/TwitterUKdf$n.male + TwitterUKdf$nLIWC.female/TwitterUKdf$n.female
TwitterUKdf$w <- rollmean(TwitterUKdf$signal, k=7, align="right", na.pad = T)
Yougovdf$r <- Yougovdf$scared/100
Twittersel <- left_join(Yougovdf, TwitterUKdf, by="day")

Tdf <- read.csv("Data/genderAuthors-total10K.csv")
Tdf2 <- read.csv("Data/genderAuthors-anxiety10K.csv")
TwitterUKdf10K <- inner_join(Tdf, Tdf2, by="day")
names(TwitterUKdf10K) <- c("day", "n.male", "n.female", "nLIWC.male",  "nLIWC.female")
TwitterUKdf10K$signal <- TwitterUKdf10K$nLIWC.male/TwitterUKdf10K$n.male + TwitterUKdf10K$nLIWC.female/TwitterUKdf10K$n.female
TwitterUKdf10K$w10K <- rollmean(TwitterUKdf10K$signal, k=7, align="right", na.pad = T)

Twittersel <- inner_join(Twittersel, TwitterUKdf10K, by="day")

cor.test(Twittersel$r, Twittersel$w)
cor.test(Twittersel$r, Twittersel$w10K)
r.test(n=nrow(Twittersel), r12=cor(Twittersel$r,Twittersel$w10K), r13=cor(Twittersel$r, Twittersel$w), r23=cor(Twittersel$w, Twittersel$w10K), twotailed = F)
```
