---
title: 
date: 
author: 
output: 
  pdf_document:
    keep_tex: true
---

```{r, echo=FALSE, message=FALSE, results='hide', cache=T}
Sys.setlocale("LC_TIME", "en_US.UTF-8")

library(dplyr) #dplyr_1.0.3
library(ggplot2) #ggplot2_3.3.2
library(ggpubr) #ggpubr_0.4.0
library(readxl) #readxl_1.3.1
library(zoo) #zoo_1.8-8
library(DCCA) #DCCA_0.1.1 
library(sandwich) #sandwich_3.0-1
library(tseries) #tseries_0.10-47
library(lmtest) #lmtest_0.9-38 
library(knitr) #knitr_1.30
library(psych) #psych_2.1.6
options(scipen = 10)

source("Functions.R")
R <- 10000
```

```{r}
#download.file("https://yougov.co.uk/_pubapis/v5/uk/trackers/britains-mood-measured-weekly/download/", destfile="YouGov/britains-mood-measured-weekly.xlsx")
Yougovdf <- read_excel("yougovoutput.xlsx", sheet="yougovoutput")
names(Yougovdf)[1] <- "day"

```

```{r}
#result <- t(read_excel("single/single_quary_epoch2.xlsx"))
#result <- read.csv(file="output.csv")
#names(result) <- c("day", "bert.result")
#result$ro <- rollmean(result$bert.result, k=7, align="right", na.pad = T)
epoch<-2
query_type<-"Single"
similarity<-"Sim"
#filename<-getfilename(epoch, query_type,similarity)
filename <-"Result/baseline_same_model.xlsx"
berd <- read_excel(filename,sheet="transpose")
names(berd)[1] <- "day"
#Yougovdf$day <- as.Date(Yougovdf$day)
Yougovdf$day <- Yougovdf$day
joind = inner_join(Yougovdf, berd, by="day")
#berdsad$value_column[is.na(berdsad$value_column)] <- mean(berdsad$value_column, na.rm = TRUE)
```

Sad with similarity

``` r
```

```{r}
Emotion<-"Sad"
label <- paste(Emotion," in Yougov and ",Emotion," in Bertweet (Type: Base Model)")
joind$x <- joind$Sad.x
joind$y <- joind$Sad.y

joind$y <- rollmean(joind$y, k=7, align="right", na.pad = T)
joind <- na.omit(joind)
y_label<-paste("Rescaled ",Emotion)
plotTS(joind, joind, "x", "y",  "darkred", "darkblue","Yougov", "Base Model", title=label, ylab=y_label, ymin=-2.5, ymax=5,label) 
#capture.output({
results <- analyses(joind, joind, R,label)
results$emotion  <- Emotion
results$method <- "Bert"
results$reweight <- "Yes"
results <- results[, c(16,17,18, seq(1,15))]
#}, file = 'file.txt')
```

Happy with similartiy

```{r}
Emotion<-"Happy"
label <- paste(Emotion," in Yougov and ",Emotion," in Bertweet (Type: Base Model)")
joind$x <- joind$Happy.x
joind$y <- joind$Happy.y

joind$y <- rollmean(joind$y, k=7, align="right", na.pad = T)
joind <- na.omit(joind)
y_label<-paste("Rescaled ",Emotion)
plotTS(joind, joind, "x", "y",  "darkred","darkblue", "Yougov", "Base Model", title=label, ylab=y_label, ymin=-2.5, ymax=5,label) 

results <- analyses(joind, joind, R,label)
results$emotion  <- Emotion
results$method <- "Bert"
results$reweight <- "Yes"
results <- results[, c(16,17,18, seq(1,15))]
```

Stressed with similarity

```{r}
Emotion<-"Stressed"
label <- paste(Emotion," in Yougov and ",Emotion," in Bertweet (Epoch:",epoch,')',sep = "")

joind$x <- joind$Stressed.x
joind$y <- joind$Stressed.y

joind$y <- rollmean(joind$y, k=7, align="right", na.pad = T)
joind <- na.omit(joind)
y_label<-paste("Rescaled ",Emotion)
plotTS(joind, joind, "x", "y", "darkblue", "darkred", "Bert", "Yougov", title=label, ylab=y_label, ymin=-2.5, ymax=5,label) 

results <- analyses(joind, joind, R,label)
results$emotion  <- Emotion
results$method <- "Bert"
results$reweight <- "Yes"
results <- results[, c(16,17,18, seq(1,15))]
```

Frustrated

```{r}
Emotion<-"Frustrated"
label <- paste(Emotion," in Yougov and ",Emotion," in Bertweet (",query_type,' Query ',similarity," Epoch:",epoch,')',sep = "")

joind$x <- joind$Frustrated.x
joind$y <- joind$Frustrated.y

joind$y <- rollmean(joind$y, k=7, align="right", na.pad = T)
joind <- na.omit(joind)
y_label<-paste("Rescaled ",Emotion)
plotTS(joind, joind, "x", "y", "darkblue", "darkred", "Bert", "Yougov", title=label, ylab=y_label, ymin=-2.5, ymax=5,label) 
results <- analyses(joind, joind, R,label)
results$emotion  <- Emotion
results$method <- "Bert"
results$reweight <- "Yes"
results <- results[, c(16,17,18, seq(1,15))]
```

Inspired

```{r}
Emotion<-"Inspired"
label <- paste(Emotion," in Yougov and ",Emotion," in Bertweet (",query_type,' Query ',similarity," Epoch:",epoch,')',sep = "")

joind$x <- joind$Inspired.x
joind$y <- joind$Inspired.y

joind$y <- rollmean(joind$y, k=7, align="right", na.pad = T)
joind <- na.omit(joind)
y_label<-paste("Rescaled ",Emotion)
plotTS(joind, joind, "x", "y", "darkblue", "darkred", "Bert", "Yougov", title=label, ylab=y_label, ymin=-2.5, ymax=5,label) 

results <- analyses(joind, joind, R, label)
results$emotion  <- Emotion
results$method <- "Bert"
results$reweight <- "Yes"
results <- results[, c(16,17,18, seq(1,15))]

```

Apathetic

```{r}
Emotion<-"Apathetic"
label <- paste(Emotion," in Yougov and ",Emotion," in Bertweet (",query_type,' Query ',similarity," Epoch:",epoch,')',sep = "")

joind$x <- joind$Apathetic.x
joind$y <- joind$Apathetic.y

joind$y <- rollmean(joind$y, k=7, align="right", na.pad = T)
joind <- na.omit(joind)
y_label<-paste("Rescaled ",Emotion)
plotTS(joind, joind, "x", "y", "darkblue", "darkred", "Bert", "Yougov", title=label, ylab=y_label, ymin=-2.5, ymax=5,label)  

results <- analyses(joind, joind, R,label)
results$emotion  <- Emotion
results$method <- "Bert"
results$reweight <- "Yes"
results <- results[, c(16,17,18, seq(1,15))]
```

Lonely

```{r}
Emotion<-"Lonely"
label <- paste(Emotion," in Yougov and ",Emotion," in Bertweet (",query_type,' Query ',similarity," Epoch:",epoch,')',sep = "")

joind$x <- joind$Lonely.x
joind$y <- joind$Lonely.y

joind$y <- rollmean(joind$y, k=7, align="right", na.pad = T)
joind <- na.omit(joind)
y_label<-paste("Rescaled ",Emotion)
plotTS(joind, joind, "x", "y", "darkblue", "darkred", "Bert", "Yougov", title=label, ylab=y_label, ymin=-2.5, ymax=5,label) 

results <- analyses(joind, joind, R,label)
results$emotion  <- Emotion
results$method <- "Bert"
results$reweight <- "Yes"
results <- results[, c(16,17,18, seq(1,15))]
```

Optimistic

```{r}
Emotion<-"Optimistic"
label <- paste(Emotion," in Yougov and ",Emotion," in Bertweet (",query_type,' Query ',similarity," Epoch:",epoch,')',sep = "")

joind$x <- joind$Optimistic.x
joind$y <- joind$Optimistic.y

joind$y <- rollmean(joind$y, k=7, align="right", na.pad = T)
joind <- na.omit(joind)
y_label<-paste("Rescaled ",Emotion)
plotTS(joind, joind, "x", "y", "darkblue", "darkred", "Bert", "Yougov", title=label, ylab=y_label, ymin=-2.5, ymax=5,label) 

results <- analyses(joind, joind, R,label)
results$emotion  <- Emotion
results$method <- "Bert"
results$reweight <- "Yes"
results <- results[, c(16,17,18, seq(1,15))]

```

Content

```{r}
Emotion<-"Content"
label <- paste(Emotion," in Yougov and ",Emotion," in Bertweet (",query_type,' Query ',similarity," Epoch:",epoch,')',sep = "")

joind$x <- joind$Content.x
joind$y <- joind$Content.y

joind$y <- rollmean(joind$y, k=7, align="right", na.pad = T)
joind <- na.omit(joind)
y_label<-paste("Rescaled ",Emotion)
plotTS(joind, joind, "x", "y", "darkblue", "darkred", "Bert", "Yougov", title=label, ylab=y_label, ymin=-2.5, ymax=5,label) 

results <- analyses(joind, joind, R,label)
results$emotion  <- Emotion
results$method <- "Bert"
results$reweight <- "Yes"
results <- results[, c(16,17,18, seq(1,15))]
```

Energetic

```{r}
Emotion<-"Energetic"
label <- paste(Emotion," in Yougov and ",Emotion," in Bertweet (",query_type,' Query ',similarity," Epoch:",epoch,')',sep = "")

joind$x <- joind$Energetic.x
joind$y <- joind$Energetic.y

joind$y <- rollmean(joind$y, k=7, align="right", na.pad = T)
joind <- na.omit(joind)
y_label<-paste("Rescaled ",Emotion)
plotTS(joind, joind, "x", "y", "darkblue", "darkred", "Bert", "Yougov", title=label, ylab=y_label, ymin=-2.5, ymax=5,y_label) 

results <- analyses(joind, joind, R,label)
results$emotion  <- Emotion
results$method <- "Bert"
results$reweight <- "Yes"
results <- results[, c(16,17,18, seq(1,15))]
```

Frustrated

```{r}
Emotion<-"Frustrated"
label <- paste(Emotion," in Yougov and ",Emotion," in Bertweet (",query_type,' Query ',similarity," Epoch:",epoch,')',sep = "")

joind$x <- joind$Frustrated.x
joind$y <- joind$Frustrated.y

joind$y <- rollmean(joind$y, k=7, align="right", na.pad = T)
joind <- na.omit(joind)
y_label<-paste("Rescaled ",Emotion)
plotTS(joind, joind, "x", "y", "darkblue", "darkred", "Bert", "Yougov", title=label, ylab=y_label, ymin=-2.5, ymax=5,y_label) 

results <- analyses(joind, joind, R,label)
results$emotion  <- Emotion
results$method <- "Bert"
results$reweight <- "Yes"
results <- results[, c(16,17,18, seq(1,15))]
```

# Bored

```{r}
```

```{r}
Emotion<-"Bored"
label <- paste(Emotion," in Yougov and ",Emotion," in Bertweet (",query_type,' Query ',similarity," Epoch:",epoch,')',sep = "")

joind$x <- joind$Bored.x
joind$y <- joind$Bored.y

joind$y <- rollmean(joind$y, k=7, align="right", na.pad = T)
joind <- na.omit(joind)
y_label<-paste("Rescaled ",Emotion)
plotTS(joind, joind, "x", "y", "darkblue", "darkred", "Bert", "Yougov", title=label, ylab=y_label, ymin=-2.5, ymax=5,y_label) 

results <- analyses(joind, joind, R,label)
results$emotion  <- Emotion
results$method <- "Bert"
results$reweight <- "Yes"
results <- results[, c(16,17,18, seq(1,15))]
```

Scared

```         
```

```{r}
source("Functions.R")
R <- 10000
#download.file("https://yougov.co.uk/_pubapis/v5/uk/trackers/britains-mood-measured-weekly/download/", destfile="YouGov/britains-mood-measured-weekly.xlsx")
Yougovdf <- read_excel("yougovoutput.xlsx", sheet="yougovoutput")
names(Yougovdf)[1] <- "day"
```

```{r}
epoch<-2
query_type<-"Multi_mean"
similarity<-"Sim"
filename<-getfilename(epoch, query_type,similarity)
#filename <-"Result/baseline_same_model.xlsx"
berd <- read_excel(filename,sheet="transpose")
names(berd)[1] <- "day"
#Yougovdf$day <- as.Date(Yougovdf$day)
Yougovdf$day <- Yougovdf$day
joind = inner_join(Yougovdf, berd,by="day")

joind$x <- joind$Sad.x

joind$y <- joind$Sad.y
```

```{r}
epoch<-2
query_type<-"Multi_median"
similarity<-"NoSim"
filename<-getfilename(epoch, query_type,similarity)
#filename <-"Result/baseline_same_model.xlsx"
berd2 <- read_excel(filename,sheet="transpose")
names(berd2)[1] <- "day"


joind = inner_join(joind, berd2,by="day")


```

```{r}

joind$z <- joind$Sad
```

```{r}
joind$z <- rollmean(joind$z, k=7, align="right", na.pad = T)
joind$y <- rollmean(joind$y, k=3, align="right", na.pad = T)
joind$x <- rollmean(joind$x, k=7, align="right", na.pad = T)
```

```{r}
joind$y <- rollmean(joind$y, k=4, align="right", na.pad = T)
```

```         
```

```{r}
plotTS2(joind,joind, "x", "y","z", "red", "blue","gray", "yougov", "Similarity","Normal", title="Sad with similarity and without similarity", ylab="Rescaled Sadness", ymin=-2.5, ymax=5) 
```

```         
```

```{r}

epoch<-1
query_type<-"Multi_mean"
similarity<-"NoSim"
filename<-getfilename(epoch, query_type,similarity)
#filename <-"Result/baseline_same_model.xlsx"
berd3 <- read_excel(filename,sheet="transpose")
names(berd3)[1] <- "day"


joind = inner_join(joind, berd3,by="day")


```

```         
  
```

```{r}
joind$z <- joind$Sad.x.x
joind$b <- joind$Sad.y.y
#joind$b <- rollmean(joind$b, k=7, align="right", na.pad = T)
#joind$z <- rollmean(joind$z, k=7, align="right", na.pad = T)
```

```{r}
source("Functions.R")
```

```{r}
genderdf <- read.csv("Data/RobertaAggGender.csv")

genderdf %>% filter(gender=="male") -> maledf
maledf$signalM <- maledf$mnfear
genderdf %>% filter(gender=="female") -> femaledf
femaledf$signalF <- femaledf$mnfear
TwitterUKdf <- inner_join(maledf, femaledf, by="date")
TwitterUKdf$signal <- TwitterUKdf$signalF+TwitterUKdf$signalM
names(TwitterUKdf)[2] <- "day"

TwitterUKdf$w <- rollmean(TwitterUKdf$signal, k=7, align="right", na.pad = T)

#Yougovdf$r <- Yougovdf$scared/100
joind = inner_join(joind, TwitterUKdf,by="day")

```

```{r}
Tdf <- read.csv("Data/genderVolume-total.csv")
Tdf2 <- read.csv("Data/genderVolume-sadness.csv")
TwitterUKdf <- inner_join(Tdf, Tdf2, by="day")
names(TwitterUKdf) <- c("day", "n.male", "n.female", "nLIWC.male",  "nLIWC.female")
TwitterUKdf$signal <- TwitterUKdf$nLIWC.male/TwitterUKdf$n.male + TwitterUKdf$nLIWC.female/TwitterUKdf$n.female
TwitterUKdf$w <- rollmean(TwitterUKdf$signal, k=7, align="right", na.pad = T)
joind = inner_join(joind, TwitterUKdf,by="day")
joind$z <- joind$w
#joind$y <- rollmean(joind$y, k=7, align="right", na.pad = T)
#joind$x <- rollmean(joind$x, k=7, align="right", na.pad = T)
#joind$z <- rollmean(joind$z, k=7, align="right", na.pad = T)
```

```{r}

joind$y <- rollmean(joind$y, k=7, align="right", na.pad = T)
joind$x <- rollmean(joind$x, k=7, align="right", na.pad = T)
joind$z <- rollmean(joind$z, k=7, align="right", na.pad = T)
```

## Sadness without gender reweight

```{r, echo=FALSE, message=FALSE, fig.width=9, fig.height=3, cache=T}
#plotTS3(joind,"x", "y","z","b", "gray", "red","blue","gold", "Yougov", " Single","Single","Multi", title="Sad in Yougov, Bertweet", ylab="Rescaled Sadness", ymin=-5, ymax=5) 
plotTS2(joind,joind, "x", "y","z", "red", "blue","gold", "yougov", "bert","base", title="Happy in Yougov, Bertweet, and base model 3 RoBERTa", ylab="Rescaled Sadness", ymin=-2.5, ymax=5) 
```

```{r}
# Define parameters
epoch <- 2
query_type <- "Multi_mean"
similarity <- "Sim"

# Load berd2 dataset
filename <- getfilename(epoch, query_type, similarity)
berd2 <- read_excel(filename, sheet = "transpose")
names(berd2)[1] <- "day"

# Merge Yougovdf and berd2
joind <- inner_join(Yougovdf, berd2, by = "day")

# Update similarity for new dataset
epoch <- 2
query_type <- "Multi_mean"
similarity <- "NoSim"
filename <- getfilename(epoch, query_type, similarity)

# Load berd dataset and merge
berd <- read_excel(filename, sheet = "transpose")
names(berd)[1] <- "day"
joind2 <- inner_join(Yougovdf, berd, by = "day")

# Compute rolling mean
#joind$x <- rollmean(Yougovdf$Sad,  k = 7, align = "right", na.pad = TRUE)


# Reload berd3 dataset and merge
epoch <- 2
query_type <- "Multi_mean"
similarity <- "NoSim"
filename <- getfilename(epoch, query_type, similarity)
berd3 <- read_excel(filename, sheet = "transpose")
names(berd3)[1] <- "day"
joind3 <- inner_join(Yougovdf, berd3, by = "day")

# Compute additional rolling means


joind$y <- rollmean(joind$Happy.y, k = 7, align = "right", na.pad = TRUE)
joind$z <- rollmean(joind2$Happy.y, k = 7, align = "right", na.pad = TRUE)
joind$b <- rollmean(joind3$Happy.y, k = 7, align = "right", na.pad = TRUE)
# Compute rolling mean
joind$x <- rollmean(joind$Happy.x,  k = 7, align = "right", na.pad = TRUE)

# Plot results
plotTS2(joind,joind, "x", "y", "z", 
        "green", "red", "blue", 
        "Yougov", "Epoch 1", "Epoch 2",
        title = "Sad in Yougov, Bertweet",
        ylab = "Rescaled Sadness",
        ymin = -5, ymax = 5)
```

## Sadness: men

```         
joind$y <- rollmean(joind$y, k=7, align="right", na.pad = T)
```

```{r}
epoch<-1
query_type<-"Multi_mean"
similarity<-"Sim"
filename<-getfilename(epoch, query_type,similarity)
#filename <-"Result/baseline_same_model.xlsx"
berd <- read_excel(filename,sheet="transpose")
names(berd)[1] <- "day"


```

```{r}
epoch<-1
query_type<-"Multi_mean"
similarity<-"NoSim"
filename<-getfilename(epoch, query_type,similarity)
#filename <-"Result/baseline_same_model.xlsx"
berd2 <- read_excel(filename,sheet="transpose")
names(berd2)[1] <- "day"
joind2 = inner_join(Yougovdf, berd,by="day")
joind2 = inner_join(joind2, berd2,by="day")

```

```{r}

joind2$x <- joind2$Sad.x
joind2$y <- joind2$Sad.y
joind2$a <- joind2$Sad
#joind2$y <- rollmean(joind2$y, k=7, align="right", na.pad = T)
#joind2$a <- rollmean(joind2$a, k=7, align="right", na.pad = T)
```

```{r}
plotTS2(joind2,joind2, "x", "y","a", "red", "blue","gold", "yougov", "bert","base", title="Happy in Yougov, Bertweet, and base model 1", ylab="Rescaled Sadness", ymin=-2.5, ymax=5) 
```

## Sadness: women

```         
```

## Sadness Roberta

```{r, echo=FALSE, message=FALSE, fig.width=5, fig.height=3.5, cache=T}
genderdf <- read.csv("Data/RobertaAggGender.csv")

genderdf %>% filter(gender=="male") -> maledf
maledf$signalM <- maledf$mnsadness
genderdf %>% filter(gender=="female") -> femaledf
femaledf$signalF <- femaledf$mnsadness
TwitterUKdf <- inner_join(maledf, femaledf, by="date")
TwitterUKdf$signal <- TwitterUKdf$signalF+TwitterUKdf$signalM
names(TwitterUKdf)[2] <- "day"

TwitterUKdf$w <- rollmean(TwitterUKdf$signal, k=7, align="right", na.pad = T)

Yougovdf$r <- Yougovdf$sad/100

Twittersel <- left_join(Yougovdf, TwitterUKdf, by="day")
Twittersel$r <- Twittersel$w

plotTS(Twittersel, Yougovdf, "r", "r","darkorange", "darkred","Twitter", "Yougov", title="Sad in Yougov and Sad in Twitter (Roberta)", ylab="Rescaled Sadness", ymin=-2.5, ymax=5) 

nres <- analyses(Twittersel, Yougovdf, R)
nres$emotion  <- "sadness"
nres$method <- "RoBERTa"
nres$reweight <- "Yes"
results <- rbind(results, nres)
```

## Sadness Roberta without gender reweight

```{r, echo=FALSE, message=FALSE, fig.width=9, fig.height=3, cache=T}
Tdf <- read.csv("Data/RobertaAgg.csv")
TwitterUKdf <- data.frame(Tdf$date, Tdf$n, Tdf$mnsadness)
names(TwitterUKdf) <- c("day", "n", "signal")
TwitterUKdf$w <- rollmean(TwitterUKdf$signal, k=7, align="right", na.pad = T)

Yougovdf$r <- Yougovdf$sad/100

Twittersel <- left_join(Yougovdf, TwitterUKdf, by="day")
Twittersel$r <- Twittersel$w

nres <- analyses(Twittersel, Yougovdf, R)
nres$emotion  <- "sadness"
nres$method <- "RoBERTa"
nres$reweight <- "No"
results <- rbind(results, nres)
```

\newpage

# Scared

```{r, echo=FALSE, message=FALSE, fig.width=5, fig.height=3.5, cache=T}
Tdf <- read.csv("Data/genderVolume-total.csv")
Tdf2 <- read.csv("Data/genderVolume-anxiety.csv")
TwitterUKdf <- inner_join(Tdf, Tdf2, by="day")
names(TwitterUKdf) <- c("day", "n.male", "n.female", "nLIWC.male",  "nLIWC.female")
TwitterUKdf$signal <- TwitterUKdf$nLIWC.male/TwitterUKdf$n.male + TwitterUKdf$nLIWC.female/TwitterUKdf$n.female
TwitterUKdf$w <- rollmean(TwitterUKdf$signal, k=7, align="right", na.pad = T)

Yougovdf$r <- Yougovdf$scared/100

Twittersel <- left_join(Yougovdf, TwitterUKdf, by="day")
Twittersel$r <- Twittersel$w

plotTS(Twittersel, Yougovdf, "r", "r", "darkblue", "darkred", "Twitter", "Yougov", title="Scared in Yougov and Anxiety in Twitter (LIWC)", ylab="Rescaled Anxiety", ymin=-2.5, ymax=7.5) 

nres <- analyses(Twittersel, Yougovdf, R)
nres$emotion  <- "anxiety"
nres$method <- "LIWC"
nres$reweight <- "Yes"
results <- rbind(results, nres)
```

## Scared without gender reweight

```{r, echo=FALSE, message=FALSE, fig.width=9, fig.height=3, cache=T}
Tdf <- read.csv("Data/Volume-total.csv")
Tdf2 <- read.csv("Data/Volume-anxiety.csv")
TwitterUKdf <- inner_join(Tdf, Tdf2, by="day")
names(TwitterUKdf) <- c("day", "n", "nAnxLIWC")
TwitterUKdf$signal <- TwitterUKdf$nAnxLIWC/TwitterUKdf$n
TwitterUKdf$w <- rollmean(TwitterUKdf$signal, k=7, align="right", na.pad = T)

Yougovdf$r <- Yougovdf$scared/100

Twittersel <- left_join(Yougovdf, TwitterUKdf, by="day")
Twittersel$r <- Twittersel$w

nres <- analyses(Twittersel, Yougovdf, R)
nres$emotion  <- "anxiety"
nres$method <- "LIWC"
nres$reweight <- "No"
results <- rbind(results, nres)
```

## Scared: men

```{r, echo=FALSE, message=FALSE, fig.width=9, fig.height=3, cache=T}
Tdf <- read.csv("Data/genderVolume-total.csv")
Tdf2 <- read.csv("Data/genderVolume-anxiety.csv")
TwitterUKdf <- inner_join(Tdf, Tdf2, by="day")
names(TwitterUKdf) <- c("day", "n.male", "n.female", "nLIWC.male",  "nLIWC.female")
TwitterUKdf$signal <- TwitterUKdf$nLIWC.male/TwitterUKdf$n.male
TwitterUKdf$w <- rollmean(TwitterUKdf$signal, k=7, align="right", na.pad = T)

Mdf$r <- Mdf$scared/100

Twittersel <- left_join(Mdf, TwitterUKdf, by="day")
Twittersel$r <- Twittersel$w

nres <- analyses(Twittersel, Mdf, R)
nres$emotion <- "anxiety"
nres$gender <- "male"
genderresults <- rbind(genderresults, nres)
```

## Scared: women

```{r, echo=FALSE, message=FALSE, fig.width=9, fig.height=3, cache=T}
TwitterUKdf$signal <- TwitterUKdf$nLIWC.female/TwitterUKdf$n.female
TwitterUKdf$w <- rollmean(TwitterUKdf$signal, k=7, align="right", na.pad = T)

Fdf$r <- Fdf$scared/100

Twittersel <- left_join(Fdf, TwitterUKdf, by="day")
Twittersel$r <- Twittersel$w


nres <- analyses(Twittersel, Fdf, R)
nres$emotion <- "anxiety"
nres$gender <- "female"
genderresults <- rbind(genderresults, nres)
```

## Scared Roberta

```{r, echo=FALSE, message=FALSE, fig.width=5, fig.height=3.5, cache=T}
genderdf <- read.csv("Data/RobertaAggGender.csv")

genderdf %>% filter(gender=="male") -> maledf
maledf$signalM <- maledf$mnfear
genderdf %>% filter(gender=="female") -> femaledf
femaledf$signalF <- femaledf$mnfear
TwitterUKdf <- inner_join(maledf, femaledf, by="date")
TwitterUKdf$signal <- TwitterUKdf$signalF+TwitterUKdf$signalM
names(TwitterUKdf)[2] <- "day"

TwitterUKdf$w <- rollmean(TwitterUKdf$signal, k=7, align="right", na.pad = T)

Yougovdf$r <- Yougovdf$scared/100

Twittersel <- left_join(Yougovdf, TwitterUKdf, by="day")
Twittersel$r <- Twittersel$w

plotTS(Twittersel, Yougovdf, "r", "r", "darkorange", "darkred", "Twitter", "Yougov", title="Scared in Yougov and Fear in Twitter (Roberta)", ylab="Rescaled Fear", ymin=-2.5, ymax=7.5) 


nres <- analyses(Twittersel, Yougovdf, R)
nres$emotion  <- "anxiety"
nres$method <- "RoBERTa"
nres$reweight <- "Yes"
results <- rbind(results, nres)
```

## Scared Roberta without gender reweight

```{r, echo=FALSE, message=FALSE, fig.width=9, fig.height=3, cache=T}
Tdf <- read.csv("Data/RobertaAgg.csv")
TwitterUKdf <- data.frame(Tdf$date, Tdf$n, Tdf$mnfear)
names(TwitterUKdf) <- c("day", "n", "signal")
TwitterUKdf$w <- rollmean(TwitterUKdf$signal, k=7, align="right", na.pad = T)

Yougovdf$r <- Yougovdf$scared/100

Twittersel <- left_join(Yougovdf, TwitterUKdf, by="day")
Twittersel$r <- Twittersel$w

nres <- analyses(Twittersel, Yougovdf, R)
nres$emotion  <- "anxiety"
nres$method <- "RoBERTa"
nres$reweight <- "No"
results <- rbind(results, nres)
```

\newpage

# Happy

```{r, echo=FALSE, message=FALSE, fig.width=5, fig.height=3.5, cache=T}
Tdf <- read.csv("Data/genderVolume-total.csv")
Tdf2 <- read.csv("Data/genderVolume-posemo.csv")
TwitterUKdf <- inner_join(Tdf, Tdf2, by="day")
names(TwitterUKdf) <- c("day", "n.male", "n.female", "nLIWC.male",  "nLIWC.female")
TwitterUKdf$signal <- TwitterUKdf$nLIWC.male/TwitterUKdf$n.male + TwitterUKdf$nLIWC.female/TwitterUKdf$n.female
TwitterUKdf$w <- rollmean(TwitterUKdf$signal, k=7, align="right", na.pad = T)

Yougovdf$r <- Yougovdf$happy/100

Twittersel <- left_join(Yougovdf, TwitterUKdf, by="day")
Twittersel$r <- Twittersel$w

plotTS(Twittersel, Yougovdf, "r", "r", "darkblue", "darkred",  "Twitter", "Yougov", title="Happy in Yougov and Positive in Twitter (LIWC)", ylab="Rescaled Positive", ymin=-3.5, ymax=4)

nres <- analyses(Twittersel, Yougovdf, R)
nres$emotion  <- "joy"
nres$method <- "LIWC"
nres$reweight <- "Yes"
results <- rbind(results, nres)
```

## Happy without gender reweight

```{r, echo=FALSE, message=FALSE, fig.width=9, fig.height=3, cache=T}
Tdf <- read.csv("Data/Volume-total.csv")
Tdf2 <- read.csv("Data/Volume-posemo.csv")
TwitterUKdf <- inner_join(Tdf, Tdf2, by="day")
names(TwitterUKdf) <- c("day", "n", "nPosLIWC")
TwitterUKdf$signal <- TwitterUKdf$nPosLIWC/TwitterUKdf$n
TwitterUKdf$w <- rollmean(TwitterUKdf$signal, k=7, align="right", na.pad = T)

Yougovdf$r <- Yougovdf$happy/100

Twittersel <- left_join(Yougovdf, TwitterUKdf, by="day")
Twittersel$r <- Twittersel$w

nres <- analyses(Twittersel, Yougovdf, R)
nres$emotion  <- "joy"
nres$method <- "LIWC"
nres$reweight <- "No"
results <- rbind(results, nres)
```

## Happy: men

```{r, echo=FALSE, message=FALSE, fig.width=9, fig.height=3, cache=T}
Tdf <- read.csv("Data/genderVolume-total.csv")
Tdf2 <- read.csv("Data/genderVolume-posemo.csv")
TwitterUKdf <- inner_join(Tdf, Tdf2, by="day")
names(TwitterUKdf) <- c("day", "n.male", "n.female", "nLIWC.male",  "nLIWC.female")
TwitterUKdf$signal <- TwitterUKdf$nLIWC.male/TwitterUKdf$n.male
TwitterUKdf$w <- rollmean(TwitterUKdf$signal, k=7, align="right", na.pad = T)

Mdf$r <- Mdf$happy/100

Twittersel <- left_join(Mdf, TwitterUKdf, by="day")
Twittersel$r <- Twittersel$w

nres <- analyses(Twittersel, Mdf, R)
nres$emotion <- "joy"
nres$gender <- "male"
genderresults <- rbind(genderresults, nres)
```

## Happy: women

```{r, echo=FALSE, message=FALSE, fig.width=9, fig.height=3, cache=T}
TwitterUKdf$signal <- TwitterUKdf$nLIWC.female/TwitterUKdf$n.female
TwitterUKdf$w <- rollmean(TwitterUKdf$signal, k=7, align="right", na.pad = T)

Fdf$r <- Fdf$happy/100

Twittersel <- left_join(Fdf, TwitterUKdf, by="day")
Twittersel$r <- Twittersel$w

nres <- analyses(Twittersel, Fdf, R)
nres$emotion <- "joy"
nres$gender <- "female"
genderresults <- rbind(genderresults, nres)

```

## Happy Roberta

```{r, echo=FALSE, message=FALSE, fig.width=5, fig.height=3.5, cache=T}
genderdf <- read.csv("Data/RobertaAggGender.csv")

genderdf %>% filter(gender=="male") -> maledf
maledf$signalM <- maledf$mnjoy
genderdf %>% filter(gender=="female") -> femaledf
femaledf$signalF <- femaledf$mnjoy
TwitterUKdf <- inner_join(maledf, femaledf, by="date")
TwitterUKdf$signal <- TwitterUKdf$signalF+TwitterUKdf$signalM
names(TwitterUKdf)[2] <- "day"

TwitterUKdf$w <- rollmean(TwitterUKdf$signal, k=7, align="right", na.pad = T)

Yougovdf$r <- Yougovdf$happy/100

Twittersel <- left_join(Yougovdf, TwitterUKdf, by="day")
Twittersel$r <- Twittersel$w

plotTS(Twittersel, Yougovdf, "r", "r", "darkorange", "darkred", "Twitter", "Yougov", title="Happy in Yougov and Joy in Twitter (Roberta)", ylab="Rescaled Joy", ymin=-3.5, ymax=4)


nres <- analyses(Twittersel, Yougovdf, R)
nres$emotion  <- "joy"
nres$method <- "RoBERTa"
nres$reweight <- "Yes"
results <- rbind(results, nres)
```

## Happy Roberta without gender reweight

```{r, echo=FALSE, message=FALSE, fig.width=9, fig.height=3, cache=T}
Tdf <- read.csv("Data/RobertaAgg.csv")
TwitterUKdf <- data.frame(Tdf$date, Tdf$n, Tdf$mnjoy)
names(TwitterUKdf) <- c("day", "n", "signal")
TwitterUKdf$w <- rollmean(TwitterUKdf$signal, k=7, align="right", na.pad = T)

Yougovdf$r <- Yougovdf$happy/100

Twittersel <- left_join(Yougovdf, TwitterUKdf, by="day")
Twittersel$r <- Twittersel$w

nres <- analyses(Twittersel, Yougovdf, R)
nres$emotion  <- "joy"
nres$method <- "RoBERTa"
nres$reweight <- "No"
results <- rbind(results, nres)
```

# Summary macroscopes

```{r, echo=FALSE, message=FALSE, fig.width=9, fig.height=3, cache=T}
results %>% select(emotion, method, reweight, rh, rhlow, rhhigh, rhp, rhpperm, rp, rplow, rphigh, rpp, rppperm)%>% kable(digits=3)

results %>% select(emotion, method, reweight, dcca, dccap, beta, betap, KSp)%>% kable(digits=3)

genderresults %>% select(emotion, gender, rh, rhlow, rhhigh, rhp, rhpperm, rp, rplow, rphigh, rpp, rppperm)%>% kable(digits=3)

genderresults %>% select(emotion, gender, dcca, dccap, beta, betap, KSp)%>% kable(digits=3)
```

# YouGov and I feel

```{r, echo=FALSE, message=FALSE, fig.width=9, fig.height=3, cache=T}
corrsdf <- NULL

inds <- c("happy","sad","energetic","apathetic","inspired","frustrated","optimistic", "stressed","content","bored","lonely","scared")

for (ind in inds)
{
print(ind)
Yougovdf$r <- Yougovdf[[ind]]/100

Tdf <- read.csv("Data/Volume-total.csv")
Tdf2 <- read.csv(paste0("Data/Volume-",ind,"YouGov.csv"))
TwitterUKdf <- inner_join(Tdf, Tdf2, by="day")
names(TwitterUKdf) <- c("day", "n", "ntweets")
TwitterUKdf$signal <- TwitterUKdf$ntweets/TwitterUKdf$n
TwitterUKdf$w <- rollmean(TwitterUKdf$signal, k=7, align="right", na.pad = T)
TwitterUKdf$ntweetstotal <- rollsum(TwitterUKdf$ntweets, k=7, align="right", na.pad = T)

Twittersel <- left_join(Yougovdf, TwitterUKdf, by="day")
Twittersel$r <- Twittersel$w

X <- Twittersel$r
Y <- Yougovdf$r
ct <- cor.test(X,Y)
print(ct)

print("Corr perm test p-val:")
rndR <- permcor(X,Y,R) # do a permutation test 
print((sum(rndR>=cor(X,Y))+1)/R)

corrsdf <- rbind(corrsdf, data.frame(ind, cor=ct$estimate, corlow = ct$conf.int[1], corhigh = ct$conf.int[2], YGmean=mean(Yougovdf$r), TWmean=mean(Twittersel$ntweetstotal)))

}
```

```{r, echo=FALSE, message=FALSE, fig.width=9, fig.height=3, cache=T, results='asis'}
kable(corrsdf)
```

```{r, echo=FALSE, message=FALSE, fig.width=7, fig.height=3.5, cache=T}
corrsdf$emotion <- corrsdf$ind

ggplot(corrsdf, aes(x=reorder(emotion, cor), y=cor, fill=as.numeric(reorder(emotion, cor))-6, group=emotion)) + 
  geom_col(stat="identity", color="black", 
           position=position_dodge())  +  scale_fill_gradient2(low='blue', mid="purple", high='red') +
  geom_errorbar(aes(ymin=corlow, ymax=corhigh), width=.2,
                 position=position_dodge(.9))  + coord_flip() + theme_bw()


```

## With gender rescaling

```{r, echo=FALSE, message=FALSE, fig.width=9, fig.height=3, cache=T}
corrsdf <- NULL

inds <- c("happy","sad","energetic","apathetic","inspired","frustrated","optimistic", "stressed","content","bored","lonely","scared")

for (ind in inds)
{
print(ind)
Yougovdf$r <- Yougovdf[[ind]]/100

Tdf <- read.csv("Data/genderVolume-total.csv")
Tdf2 <- read.csv(paste0("Data/genderVolume-",ind,"YouGov.csv"))
TwitterUKdf <- inner_join(Tdf, Tdf2, by="day")
names(TwitterUKdf) <- c("day", "maletotal", "femaletotal","male", "female")
TwitterUKdf$signal <- TwitterUKdf$male/TwitterUKdf$maletotal + TwitterUKdf$female/TwitterUKdf$femaletotal
TwitterUKdf$w <- rollmean(TwitterUKdf$signal, k=7, align="right", na.pad = T)

Twittersel <- left_join(Yougovdf, TwitterUKdf, by="day")
Twittersel$r <- Twittersel$w

X <- Twittersel$r
Y <- Yougovdf$r
ct <- cor.test(X,Y)
print(ct)

print("Corr perm test p-val:")
rndR <- permcor(X,Y,R) # do a permutation test 
print((sum(rndR>=cor(X,Y))+1)/R)

corrsdf <- rbind(corrsdf, data.frame(ind, cor=ct$estimate, corlow = ct$conf.int[1], corhigh = ct$conf.int[2], YGmean=mean(Yougovdf$r)))

}


```

```{r, echo=FALSE, message=FALSE, fig.width=9, fig.height=3, cache=T, results='asis'}
kable(corrsdf)
```

```{r, echo=FALSE, message=FALSE, fig.width=7, fig.height=3.5, cache=T}
corrsdf$emotion <- corrsdf$ind

ggplot(corrsdf, aes(x=reorder(emotion, cor), y=cor, fill=as.numeric(reorder(emotion, cor))-6, group=emotion)) + 
  geom_col(stat="identity", color="black", 
           position=position_dodge())  +  scale_fill_gradient2(low='blue', mid="purple", high='red') +
  geom_errorbar(aes(ymin=corlow, ymax=corhigh), width=.2,
                 position=position_dodge(.9))  + coord_flip() + theme_bw()
```

# Social signals as 3rd person

```{r, echo=FALSE, message=FALSE, results='hide', cache=T, eval=F}
Yougovdf <- processYouGov(file="YouGov/britains-mood-measured-weekly.xlsx", sheet="All adults")
names(Yougovdf)[1] <- "day"

Tdf <- read.csv("TwitterAggregates/Volume-total.csv")

Tdf2 <- read.csv("TwitterAggregates/Volume-sadness.csv")
names(Tdf2) <- c("day", "nsad")
Tdf <- inner_join(Tdf, Tdf2)

Tdf2 <- read.csv("TwitterAggregates/Volume-anxiety.csv")
names(Tdf2) <- c("day", "nanx")
Tdf <- inner_join(Tdf, Tdf2)

Tdf2 <- read.csv("TwitterAggregates/Volume-posemo.csv")
names(Tdf2) <- c("day", "npos")
Tdf <- inner_join(Tdf, Tdf2)

Tdf2 <- read.csv("TwitterAggregates/Volume-3rdperson.csv")
names(Tdf2) <- c("day", "n3rd")
Tdf <- inner_join(Tdf, Tdf2)

Tdf2 <- read.csv("TwitterAggregates/Volume-3rdpersonanx.csv")
names(Tdf2) <- c("day", "n3rdanx")
Tdf <- inner_join(Tdf, Tdf2)

Tdf2 <- read.csv("TwitterAggregates/Volume-3rdpersonsad.csv")
names(Tdf2) <- c("day", "n3rdsad")
Tdf <- inner_join(Tdf, Tdf2)

Tdf2 <- read.csv("TwitterAggregates/Volume-3rdpersonposemo.csv")
names(Tdf2) <- c("day", "n3rdpos")
Tdf <- inner_join(Tdf, Tdf2)

Tdf %>% filter(as.Date(day)>min(as.Date(Yougovdf$day))-7 & as.Date(day) <= max(as.Date(Yougovdf$day))) -> Tdf
```

```{r, echo=FALSE, message=FALSE, cache=T, eval=F}
print("Total fraction of 3rd person tweets:")
sum(Tdf$n3rd)/sum(Tdf$ntweets)

print("Total fraction of 3rd person tweets in anxiety:")
n3rd <- sum(Tdf$n3rdanx)/sum(Tdf$nanx)
n3rd

print("Total fraction of 3rd person tweets in not anxiety:")
n3rdnot <- sum(Tdf$n3rd-Tdf$n3rdanx)/sum(Tdf$ntweets-Tdf$nanx)
n3rdnot

print("% diff:")
(n3rd-n3rdnot)/n3rdnot*100
prop.test(c(sum(Tdf$n3rdanx),sum(Tdf$n3rd-Tdf$n3rdanx)) , c(sum(Tdf$nanx), sum(Tdf$ntweets-Tdf$nanx)))

print("Total fraction of 3rd person tweets in sadness:")
n3rd <- sum(Tdf$n3rdsad)/sum(Tdf$nsad)
n3rd

print("Total fraction of 3rd person tweets in not sadness:")
n3rdnot <- sum(Tdf$n3rd-Tdf$n3rdsad)/sum(Tdf$ntweets-Tdf$nsad)
n3rdnot

print("% diff:")
(n3rd-n3rdnot)/n3rdnot*100
prop.test(c(sum(Tdf$n3rdsad),sum(Tdf$n3rd-Tdf$n3rdsad)) , c(sum(Tdf$nsad), sum(Tdf$ntweets-Tdf$nsad)))



print("Total fraction of 3rd person tweets in positive:")
n3rd <- sum(Tdf$n3rdpos)/sum(Tdf$npos)
n3rd

print("Total fraction of 3rd person tweets in not positive:")
n3rdnot <- sum(Tdf$n3rd-Tdf$n3rdpos)/sum(Tdf$ntweets-Tdf$npos)
n3rdnot

print("% diff:")
(n3rd-n3rdnot)/n3rdnot*100
prop.test(c(sum(Tdf$n3rdpos),sum(Tdf$n3rd-Tdf$n3rdpos)) , c(sum(Tdf$npos), sum(Tdf$ntweets-Tdf$npos)))


```

```{r, echo=FALSE, message=FALSE, cache=T, eval=F}
df <- read.csv("TwitterAggregates/LIWC_NER.csv")

print("Total fraction of 3rd person tweets (NER):")
sum(df$ref)/nrow(df)

print("Total fraction of 3rd person tweets in anxiety:")
f <- df$anx>0
n3rd <- sum(df$ref[f])/sum(f)
n3rd

print("Total fraction of 3rd person tweets in not anxiety:")
f <- df$anx==0
n3rdnot <- sum(df$ref[f])/sum(f)
n3rdnot

print("% diff:")
(n3rd-n3rdnot)/n3rdnot*100
prop.test(c(sum(df$ref[df$anx>0]),sum(df$ref[df$anx==0])) , c(sum(df$anx>0), sum(df$anx==0)))

print("Total fraction of 3rd person tweets in sadness:")
f <- df$sad>0
n3rd <- sum(df$ref[f])/sum(f)
n3rd

print("Total fraction of 3rd person tweets in not sadness:")
f <- df$sad==0
n3rdnot <- sum(df$ref[f])/sum(f)
n3rdnot

print("% diff:")
(n3rd-n3rdnot)/n3rdnot*100
prop.test(c(sum(df$ref[df$sad>0]),sum(df$ref[df$sad==0])) , c(sum(df$sad>0), sum(df$sad==0)))

print("Total fraction of 3rd person tweets in positive:")
f <- df$posemo>0
n3rd <- sum(df$ref[f])/sum(f)
n3rd

print("Total fraction of 3rd person tweets in not positive:")
f <- df$posemo==0
n3rdnot <- sum(df$ref[f])/sum(f)
n3rdnot


print("% diff:")
(n3rd-n3rdnot)/n3rdnot*100
prop.test(c(sum(df$ref[df$posemo>0]),sum(df$ref[df$posemo==0])) , c(sum(df$posemo>0), sum(df$posemo==0)))

```

# Election poll correlations

```{r, echo=FALSE, message=FALSE, cache=T}
df <- read.csv("Data/USPollsAligned.csv")
cor.test(df$YouGovBiden, df$HillBiden)
cor.test(df$YouGovTrump, df$HillTrump)

cor.test(df$YouGovBiden, df$RasmussenBiden)
cor.test(df$YouGovTrump, df$RasmussenTrump)

cor.test(df$RasmussenBiden, df$HillBiden)
cor.test(df$RasmussenTrump, df$HillTrump)
```

# LIWC 3rd person analysis

```{r, echo=FALSE, message=FALSE, cache=T, fig.width=4, fig.height=4, results='asis'}
df <- read.csv("Data/LIWC_1M.csv", stringsAsFactors = F)

model <- glm((shehe+they)>0 ~  (anx>0) + (sad>0) + (posemo>0), df, family="binomial")
model1 <- glm((shehe+they)>0 ~ log(WC) + (anx>0) + (sad>0) + (posemo>0), df, family="binomial")
model2 <- glm((shehe+they)>0 ~ log(WC) + (adj>0), df, family="binomial")

library(texreg)
texreg(list(model, model1, model2))
```

# Analysis of central users

```{r, echo=FALSE, message=FALSE, fig.width=5, fig.height=3.5, cache=T}
Tdf <- read.csv("Data/genderVolume-total.csv")
Tdf2 <- read.csv("Data/genderVolume-sadness.csv")
TwitterUKdf <- inner_join(Tdf, Tdf2, by="day")
names(TwitterUKdf) <- c("day", "n.male", "n.female", "nLIWC.male",  "nLIWC.female")
TwitterUKdf$signal <- TwitterUKdf$nLIWC.male/TwitterUKdf$n.male + TwitterUKdf$nLIWC.female/TwitterUKdf$n.female
TwitterUKdf$w <- rollmean(TwitterUKdf$signal, k=7, align="right", na.pad = T)
Yougovdf$r <- Yougovdf$sad/100
Twittersel <- left_join(Yougovdf, TwitterUKdf, by="day")

Tdf <- read.csv("Data/genderAuthors-total10K.csv")
Tdf2 <- read.csv("Data/genderAuthors-sadness10K.csv")
TwitterUKdf10K <- inner_join(Tdf, Tdf2, by="day")
names(TwitterUKdf10K) <- c("day", "n.male", "n.female", "nLIWC.male",  "nLIWC.female")
TwitterUKdf10K$signal <- TwitterUKdf10K$nLIWC.male/TwitterUKdf10K$n.male + TwitterUKdf10K$nLIWC.female/TwitterUKdf10K$n.female
TwitterUKdf10K$w10K <- rollmean(TwitterUKdf10K$signal, k=7, align="right", na.pad = T)

Twittersel <- inner_join(Twittersel, TwitterUKdf10K, by="day")

cor.test(Twittersel$r, Twittersel$w)
cor.test(Twittersel$r, Twittersel$w10K)
r.test(n=nrow(Twittersel), r12=cor(Twittersel$r,Twittersel$w10K), r13=cor(Twittersel$r, Twittersel$w), r23=cor(Twittersel$w, Twittersel$w10K), twotailed = F)
```

```{r, echo=FALSE, message=FALSE, fig.width=5, fig.height=3.5, cache=T}
Tdf <- read.csv("Data/genderVolume-total.csv")
Tdf2 <- read.csv("Data/genderVolume-anxiety.csv")
TwitterUKdf <- inner_join(Tdf, Tdf2, by="day")
names(TwitterUKdf) <- c("day", "n.male", "n.female", "nLIWC.male",  "nLIWC.female")
TwitterUKdf$signal <- TwitterUKdf$nLIWC.male/TwitterUKdf$n.male + TwitterUKdf$nLIWC.female/TwitterUKdf$n.female
TwitterUKdf$w <- rollmean(TwitterUKdf$signal, k=7, align="right", na.pad = T)
Yougovdf$r <- Yougovdf$scared/100
Twittersel <- left_join(Yougovdf, TwitterUKdf, by="day")

Tdf <- read.csv("Data/genderAuthors-total10K.csv")
Tdf2 <- read.csv("Data/genderAuthors-anxiety10K.csv")
TwitterUKdf10K <- inner_join(Tdf, Tdf2, by="day")
names(TwitterUKdf10K) <- c("day", "n.male", "n.female", "nLIWC.male",  "nLIWC.female")
TwitterUKdf10K$signal <- TwitterUKdf10K$nLIWC.male/TwitterUKdf10K$n.male + TwitterUKdf10K$nLIWC.female/TwitterUKdf10K$n.female
TwitterUKdf10K$w10K <- rollmean(TwitterUKdf10K$signal, k=7, align="right", na.pad = T)

Twittersel <- inner_join(Twittersel, TwitterUKdf10K, by="day")

cor.test(Twittersel$r, Twittersel$w)
cor.test(Twittersel$r, Twittersel$w10K)
r.test(n=nrow(Twittersel), r12=cor(Twittersel$r,Twittersel$w10K), r13=cor(Twittersel$r, Twittersel$w), r23=cor(Twittersel$w, Twittersel$w10K), twotailed = F)
```
